### 2019-06-07 article.tex
Add article title.

%!TEX program = xelatex
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{graphicx}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\usepackage{float}

\usepackage{url}
\bibliographystyle{plain}

\usepackage{listings}

\usepackage{parskip}
\setlength{\parindent}{1em}
\linespread{1.25}

\newcommand\diff{\,\mathrm{d}}
\renewcommand{\footnoterule}{\rule{\linewidth}{0pt}}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\begin{document}
\title{Case study of Scalable Quantum Simulation of Molecular Energies}
\author{Shuhao Yang, James Mills, Shanice St John}
\date{\today}
\maketitle
\section{Introduction}
\section{History}
\cite{trabesinger2012quantum}
\section{Non-technical background}
\section{Techniques in paper}
\cite{ryabinkin2018constrained}
\section{Main Achievement of paper}
\section{Conclusion and outlook}

\bibliography{ref}
\end{document}

### 2019-06-12 article.tex
Fill in main article, two sections TBD.

@@
 \section{Introduction}
+Richard Feynman’s words are as true today as when he spoke them: “Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical, and by golly it's a wonderful problem, because it doesn't look so easy.”
+
+Simulation of physical systems is one of the most crucial practical applications of computation by far.
+On the macroscopic scale of our lives, for instance, buildings are engineered safe and cost efficient using ﬁnite element analysis and modeling.
+Aeronautics rely hugely on computational ﬂuid dynamics simulations.
+Even nuclear weapons are tested by exhaustive computational modeling.
+
+But even so, classical computation still has its limits, including cost and accuracy.
+Additionally, when it comes to simulating microscopic systems, classical technique also exhibits its downside on efficiency.
+In computational chemistry, each subatomic orbitals and their interactions needs to be considered to achieve an accurate and realistic simulation of the microscopic system.
+Since the state of one orbital can be affected by all of the others, an exponential number of states in the basis of molecular orbitals should be computed.
+This is what we call ‘many body’ problems.
+No matter how far apart two orbitals are, their quantum states cannot be described independently, the repeated interactions between particles create quantum correlations, I.e., entanglement.
+
+A more advanced computation technique is then employed, quantum computation.
+It harnesses the principles of quantum mechanics, hence solves the classically intractable problems more accurately, faster, with a fine-grained simulation.
+
+For those information in our classical computers enough to fill up the entire memory, instead, a quantum computer can only use a few quantum bits, or qubits to store them \cite{trabesinger2012quantum}.
+since the classical storage unit ‘bit’ is binary system base on 0 and 1, but quantum computer encode them into two distinguishable quantum states, and one qubit can represent multiple states once by quantum phenomenon ‘superposition’.
+similarly, if we perform a searching algorithm on a classical string, the enumerate steps would be the number of bits within this string.
+comparably, our processing step will reduce a lot more as we only need to compute once in a quantum processor.
+
 \section{History}
-\cite{trabesinger2012quantum}
+Molecules consist of various atoms and the elementary unit of an atom is electron and nucleus.
+When we consider atomic energy, electron-nuclei, electron-electron interactions must be examined.
+Molecular energy consists of interactions between multiple atoms, including interactions between electrons from different atoms, as well as nuclei.
+Molecular energy can be pictured as a large package that contains many small balls, and the sum of the energy of their collisions is the sum of interactions between atoms.
+
+Obviously, it demands massive computation to find out the package energy as it contains a huge amount of particles.
+Therefore, some approximations need to be made to simply our model, hence molecular mechanics is introduced.
+
+Molecular mechanics models molecular systems using force fields in classical mechanics.
+Three approximations were made to reduce the computational complexity.
+Each atom simulated as one particle; each particle has their designated attributes including radius, Polaris ability and a net charge; and international are treated as springs with an equilibrium distance same as bond length.
+This theory essentially simulated every element of the molecular system as fixed particles connected by strings, which largely reduces the computational complexity.
+
+A similar theory of reducing the amount of computation is called renormalisation group.
+A simple scenario is to calculate the resistance force of an iron ball in a glass of water.
+We can simply simulate every water molecule in the glass by inputting the real size of a single water molecule as one parameter.
+The sizes of the molecules can easily be another 1000 parameters as they can be quite irregular and difficult to describe.
+Forces from multiple directions of the iron ball could be another 1000 parameters.
+Inputting all parameters, modelling an iron ball and simulating $10^26$ water molecules and their interactions can give the resistance force.
+Let’s say we have a supercomputer that allows tremendous amount of data processing and the result that this simulation gives coincides with experimental data perfectly.
+
+But what if we want to reduce the computational complexity?
+One solution is to reduce the number of water molecule simulated, which is feasible given the relative bigger size of the iron ball.
+To make up for the loss in number of molecules, the rest parameters can be changed.
+Let’s say we manipulated the parameters and the simulation gives slightly different solutions, but the overall trend is still the same as before.
+
+The computation complexity can still be compressed. We can repeat the process of reducing the number of molecules and adjusting the parameters, and still generate acceptable solutions.
+
+This process is called renormalisation group, and the results that this model generates is called low energy effective theory, in which the system size is reduced but the results is still acceptable and effective.
+
+We now return to the theory of molecular mechanics, it is not exactly accurate since it is restricted by parameters of equations, ie difference force fields for different atoms.
+A similar and perhaps more comprehensible explanation can be made from the theory of renormalisation group.
+While decreasing the parameters of calculation and reducing computation time, the accuracy of the result is decreasing as well.
+Molecular mechanics does the same for force fields and interactions inside the atom.
+
+Overall, the work on simulation molecular energies with classical methods is a trade off between precision and cost.
+Quantum simulation is able to contain all information relevant to the system and simulate them exactly as reality without approximations.
+
 \section{Non-technical background}
+In any quantum computing processes, the building blocks of the process are qubits.
+A qubit, or quantum bit, is the quantum analogue of the classical bit (strings of zeros and ones).
+So the qubit represents a quantum superposition or combination of a predetermined ‘0’ and a ‘1’ state.
+The quantum algorithms were run on superconducting qubits, these are a physical realisation of quantum bits based upon what are known as superconducting interference devices (SQUIDs), and attempt to find properties of the wavefunction of the molecule (in this case molecular Hydrogen).
+
+The wavefunction of a quantum system is a mathematical construct describing the state, it provides probabilities for results of particular measurements made on the state.
+In quantum chemistry the electronic structure of a molecule is described by the movement of the electrons of a collection of fixed atomic nuclei.
+And so a comprehensive description of the electronic structure encompasses the wavefunctions of all of these electrons, along with their respective energies.
+The idea that the motions of the electrons and nuclei may be considered separately is known as the Born-Oppenheimer approximation.
+It is a very useful assumption that simplifies electronic structure calculations appreciably.
+
+One of the reasons that developing new approaches to tackling electronic structure calculations are of importance is that they are extremely computationally expensive.
+Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems in nature by using quantum systems.
+A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum hardware and software that will allow for efficient quantum simulations of chemical systems.
+A problem of tantamount importance in quantum chemistry is that of finding the lowest energy eigenvalue of molecular electronic structures.
+These energy eigenvalues define a great deal of properties of interest in the molecule.
+This is of great interest in for example the development of pharmaceuticals where companies have an extremely laborious testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings and would better ensure that the pharmaceutical under development behaved as required prior to starting trials.
 \section{Techniques in paper}
@@
 \section{Conclusion and outlook}
+As this is the first scalable simulation of molecular energies on any type of quantum hardware it represents an important step in the history of quantum computing applications.
+The results indicate that for near-term quantum devices without effective error correction the adaptive approach represented by the Variational Quantum Eigensolver may have better error resilience than that of standard gate model approach represented by the Phase Estimation Algorithm.
+The expectation is that this work will pave the way for the development of further techniques for intractable calculations in quantum chemistry.
+And the final aim is that eventually these variational quantum chemistry techniques will allow for numerically exact simulations of chemical reaction rates, which are of great industrial commercial value.
+In particular, the efficiency - requiring only short state preparation and measurement procedures, and so it is without the normal substantial overhead required for quantum error correction - and robustness to error displayed by the experimental implementation of the variational quantum eigensolver technique indicates that this technique might succeed where classical techniques fail in solving traditionally intractable problems.
+
+Late last year the US passed the new National Quantum Initiative Act pledging around \$1.2 billion in funding for quantum information science.
+At a similar time the EU commission launched the €1 billion Quantum Technologies Flagship which will fund over 5000 of the top European researchers in quantum technologies over the next decade.
+In the UK, the EPSRC-backed Quantum Technology Hubs represent part of a £270 million investment to create national networks of quantum expertise.
+With this extraordinary push of late across Europe and also in the US and China, aiming to fast-track quantum technologies out of university research groups and into industrial applications, the importance of this work in quantum chemistry simulations cannot be overstated.
+As aside from the much touted almost pop-science status of quantum encryption, the myriad opportunities afforded by more efficient scalable quantum chemistry simulations looms large in garnering serious investor interest.
+The ability to run quantum simulations of the behaviour of molecules and materials is hoped offer new avenues for increasing our understanding of chemistry and enable the development of new medicines and materials in silico.
 

### 2019-06-12 article.tex
Techniques section updated.

@@
 \section{Techniques in paper}
-\cite{ryabinkin2018constrained}
+If I asked you how to make a cup of coffee, your response would go a little something like this; prepare a cup (clean of course), put a number of teaspoons of coffee (depends on how strong you like your coffee), boil the kettle, pour the hot water into the cup and lastly stir.
+You have now made your cup of instant coffee by following a set of instructions.
+
+Now, imagine that I asked you to compute the energy surface of a given molecule; how would you carry out this task?
+You would execute an algorithm that produces a numerical value.
+In Scalar Quantum of Molecular Energies two techniques used to determine the energy surface for a hydrogen molecule are discussed which are: 1) The Variational Quantum Eigensolver (VQE) and 2) The Quantum Phase Estimation Algorithm (PEA) which constitutes of the ‘original algorithm for quantum chemistry’.
+
+The VQE Algorithm
+Before we run our algorithm, it is imperative to understand that in quantum mechanics, the properties of a system are characterised by a state.
+Thus, we first need to prepare an initial state of the system (think of how you prepared the cup for the coffee following boiling water to be poured in).
+This is done by representing the state in a chosen vector v­­­­0.
+The vectors chosen are trial solution (ansatz) since solutions are not chosen in reference to any specific value as such \cite{ryabinkin2018constrained}.
+
+Once a variable is selected, we can find an estimate value of the energy corresponding to the chosen variable by measuring the average energy.
+The method utilised predicts the ground state, the lowest possible energy level of an atom.
+The value of the variable and estimate energy are then fed through a programme; this proposes settings for a new variable – let us call this variable v­­­­1.
+Comparing to our coffee example, it has been decided that either a new blend of coffee is necessary as the current coffee might be perhaps too strong!
+
+This process is repeated a number of times until the estimate energy approaches a specific value. The final result is an approximation the smallest eigenenergy.
+
+The Quantum Phase Estimation Algorithm (PEA)
+Similarly to the VQE algorithm, one must ensure that the system is prepared in an initial state, but with the exception that the state must have an sufficient overlap with the ground state.
+
 \section{Main Achievement of paper}

### 2019-06-12 article.tex
Added physics package and created boxes section

--- 2019-06-12 article.tex
@@
 \usepackage{float}
+\usepackage{physics}
 
@@
 
+\section{Technical Boxes}
+\section{VQE}
+\section{PEA}
+\section{Experimental realisation (SQUID)}
+The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of superconducting interference device or SQUID.
+It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are charge states, and the superposition of these charge states is tuned using microwave resonators.
+The Xmon qubit has a number of favourable features, which include easy fabrication, fast qubit control and long qubit coherence times.
+
+Using superconducting qubits is an appealing option for quantum hardware because it provides the scalability which is lacking for some other types of qubit.
+This is on account of the fact that for superconductivity the conduction electrons condense to a macroscopic quantum state which facilitates the creation of large integrated quantum circuits.
+
+The Xmon qubits are placed inside a dilution refrigerator which is at a temperature of 20mK.
+The inter-qubit coupling, and qubit measurement and control, are all done using microwave resonators.
+Single (or local) quantum gates are achieved using pulses of microwave radiation.
+The entanglement operation used is the controlled-Z or CZ gate, this is achieved by fixing the frequency of one qubit while adiabatically tuning the other qubit from the $\ket{11}$ state to near to the $\ket{02}$  state, which gives a relative phase shift.
+
 \bibliography{ref}

### 2019-06-12 article.tex
minor change
exp box

@@
 Forces from multiple directions of the iron ball could be another 1000 parameters.
-Inputting all parameters, modelling an iron ball and simulating $10^26$ water molecules and their interactions can give the resistance force.
+Inputting all parameters, modelling an iron ball and simulating $10^{26}$ water molecules and their interactions can give the resistance force.
 Let’s say we have a supercomputer that allows tremendous amount of data processing and the result that this simulation gives coincides with experimental data perfectly.
@@
 \section{Experimental realisation (SQUID)}
+ \fbox{\begin{minipage}[c]{32em}%
 The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of superconducting interference device or SQUID.
@@
 The entanglement operation used is the controlled-Z or CZ gate, this is achieved by fixing the frequency of one qubit while adiabatically tuning the other qubit from the $\ket{11}$ state to near to the $\ket{02}$  state, which gives a relative phase shift.
+\end{minipage}}
 

### 2019-06-15 article.tex
Finish Main sections.

@@
 
-The VQE Algorithm
+\subsection{The VQE Algorithm}
 Before we run our algorithm, it is imperative to understand that in quantum mechanics, the properties of a system are characterised by a state.
@@
 This is done by representing the state in a chosen vector v­­­­0.
-The vectors chosen are trial solution (ansatz) since solutions are not chosen in reference to any specific value as such \cite{ryabinkin2018constrained}.
+The vectors chosen are trial solution (ansatz) since solutions are not chosen in reference to any specific value as such.
 
@@
 
-The Quantum Phase Estimation Algorithm (PEA)
-Similarly to the VQE algorithm, one must ensure that the system is prepared in an initial state, but with the exception that the state must have an sufficient overlap with the ground state.
+\subsection{The Quantum Phase Estimation Algorithm (PEA)}
+Similarly to the VQE algorithm, one must ensure that the system is prepared in an initial state, but with the exception that the state must have a sufficient overlap with the ground state.
+
+Similarly, to the VQE algorithm, one must ensure that the system is prepared in an initial state, but with the exception that the state must have a sufficient overlap with the ground state.
+Once the state is prepared in our desired state, an approximation is applied to the operator.
+Consequently, the initial state is mapped onto a superposition state, a state that is made up of different vectors.
+After that, the state is acted on in turn inducing a phase on the system.
+Since the way in which the system evolves is controlled, it is now entangled with the initialised state.
+Next, we measure the phase obtained corresponding to each value of energy.
+The system as a result collapses to a single state with an associated probability.
+We repeat this algorithm for a higher number of ‘special’ qubits until the lowest eigenenergy is obtained, or more precisely the energy of the ground state.
 
 \section{Main Achievement of paper}
+As it is known, building a quantum computer comes with many challenges, one being the aspect of scalability.
+One of the advantages of using PEA to compute electronic structures of a molecule is better asymptotic scaling which would prove useful for larger molecules than Hydrogen.
+However, this is problematic as one would need to utilise more steps in the Trotterisation approximation which would in turn incur higher exponential costs.
+Hence, it was determined that a single Trotter step is not enough to accurately predict chemical rates for a Hydrogen molecule.
+In addition, for a single trotter step, each simulation using PEA was ran using different orderings of local Hamiltonians in order to find the optimal Trotter sequence for each bond length.
+For larger molecules, this is deemed intractable which becomes extremely difficult for the preprocessing requirements for a classical computer.
+
+On the contrary, VQE was proved to be more effective due to its robustness to error.
+This is due to its success in predicting the chemical dissociation rate below the chemical accuracy threshold.
+Due to its short measurement sequences, it is more viable to use VQE for quantum simulations.
+Consequently, the quantum coherence of the system would be preserved which would limit the quantum error correction.
+
+Although a quantum simulation such as the VQE is almost foolproof it may still not be adequate to calculate exact numerical solutions that are characteristic of various types of molecules and their interactions.
+Quantum computing shows promise to eliminate such errors whilst using a larger number of qubits.
+However, these factors work against each other.
+If such a machine can be built, there would be more states and thus information to manipulate whilst withstanding error.
+This could revolutionise applications such as pharmaceuticals where cures and treatments for complex or incurable diseases such as Cancer, Prion disease and so forth could be engineered.
+If (or when should I say) this is possible,  we would have a machine taking on the roles of a chemist, problem solver and designer simultaneously and combined into one entity!
 \section{Conclusion and outlook}

### 2019-06-18 article.tex
major article struc.

@@
 You would execute an algorithm that produces a numerical value.
-In Scalar Quantum of Molecular Energies two techniques used to determine the energy surface for a hydrogen molecule are discussed which are: 1) The Variational Quantum Eigensolver (VQE) and 2) The Quantum Phase Estimation Algorithm (PEA) which constitutes of the ‘original algorithm for quantum chemistry’.
+In Scalar Quantum of Molecular Energies two techniques used to determine the energy surface for a hydrogen molecule are discussed as follows:
+\begin{itemize}
+\item The Variational Quantum Eigensolver (VQE)
+\item The Quantum Phase Estimation Algorithm (PEA)
+\end{itemize}
+which constitutes of the ‘original algorithm for quantum chemistry’.
 
@@
 \subsection{The Quantum Phase Estimation Algorithm (PEA)}
-Similarly to the VQE algorithm, one must ensure that the system is prepared in an initial state, but with the exception that the state must have a sufficient overlap with the ground state.
-
 Similarly, to the VQE algorithm, one must ensure that the system is prepared in an initial state, but with the exception that the state must have a sufficient overlap with the ground state.
 Once the state is prepared in our desired state, an approximation is applied to the operator.
-Consequently, the initial state is mapped onto a superposition state, a state that is made up of different vectors.
+Consequently, the initial state is mapped onto a superposition state of various qubits, which is called the ancilla qubits.
 After that, the state is acted on in turn inducing a phase on the system.
@@
 We repeat this algorithm for a higher number of ‘special’ qubits until the lowest eigenenergy is obtained, or more precisely the energy of the ground state.
+
+\fbox{\begin{minipage}[c]{32em}%
+ \centerline{\textbf{PEA}}
+ The molecular energies can be obtained by the time evolution of molecular Hamiltonian, which is a unitary operator $U = e^{-iHt}$.
+We can first prepare an initial state that strongly overlaps the ground state of molecular hydrogen.
+As any state $\ket{\psi(t)}$ evolved by unitary $U$ can be represent by applying phase difference onto initial state $e^{-iEt}\ket{\psi(0)}$.
+Phase estimation algorithm (PEA) is used then to find this relative phase and convert it into energy.
+In order to preform PEA we need to prepare two parts of qubits.
+First n qubits of superposition state $\frac{\ket{0} + \ket{1}}{\sqrt 2}$, second, our initial state.
+Since we can evolve states by unity operator.
+By inputting both parts of qubits onto a multiple controlled-U gate, the eigenvalue of each unitary $U$ will transform to each one of qubits in first part.
+
+Now let us recap Quantum Fourier Transformation, one transforms the tensor product of multiple states onto phase of some superposition states.
+\begin{footnotesize}
+\[
+	\ket{j_{1} j_{2} \cdots j_{n}}\rightarrow \frac{\left(\ket{0}+e^{2 \pi i 0.
+j_{n}}\ket{1}\right)\left(\ket{0}+e^{2 \pi i 0.
+j_{n-1} j_{n}}\ket{1}\right) \cdots\left( \ket{0}+e^{2 \pi i 0.
+j_{1} j_{2} \cdots j_{n-1} j_{n} }\ket{1}\right)}{2^{\frac{n}{2}}}
+\] 
+\end{footnotesize}
+
+\end{minipage}}
+
+ \fbox{\begin{minipage}[c]{32em}%
+ \centerline{\textbf{Experimental realisation (SQUID)}}
+The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of superconducting interference device or SQUID.
+It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are charge states, and the superposition of these charge states is tuned using microwave resonators.
+The Xmon qubit has a number of favourable features, which include easy fabrication, fast qubit control and long qubit coherence times.
+
+Using superconducting qubits is an appealing option for quantum hardware because it provides the scalability which is lacking for some other types of qubit.
+This is on account of the fact that for superconductivity the conduction electrons condense to a macroscopic quantum state which facilitates the creation of large integrated quantum circuits.
+
+The Xmon qubits are placed inside a dilution refrigerator which is at a temperature of 20mK.
+The inter-qubit coupling, and qubit measurement and control, are all done using microwave resonators.
+Single (or local) quantum gates are achieved using pulses of microwave radiation.
+The entanglement operation used is the controlled-Z or CZ gate, this is achieved by fixing the frequency of one qubit while adiabatically tuning the other qubit from the $\ket{11}$ state to near to the $\ket{02}$  state, which gives a relative phase shift.
+\end{minipage}}
 
@@
 \section{PEA}
+
 \section{Experimental realisation (SQUID)}
- \fbox{\begin{minipage}[c]{32em}%
-The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of superconducting interference device or SQUID.
-It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are charge states, and the superposition of these charge states is tuned using microwave resonators.
-The Xmon qubit has a number of favourable features, which include easy fabrication, fast qubit control and long qubit coherence times.
-
-Using superconducting qubits is an appealing option for quantum hardware because it provides the scalability which is lacking for some other types of qubit.
-This is on account of the fact that for superconductivity the conduction electrons condense to a macroscopic quantum state which facilitates the creation of large integrated quantum circuits.
-
-The Xmon qubits are placed inside a dilution refrigerator which is at a temperature of 20mK.
-The inter-qubit coupling, and qubit measurement and control, are all done using microwave resonators.
-Single (or local) quantum gates are achieved using pulses of microwave radiation.
-The entanglement operation used is the controlled-Z or CZ gate, this is achieved by fixing the frequency of one qubit while adiabatically tuning the other qubit from the $\ket{11}$ state to near to the $\ket{02}$  state, which gives a relative phase shift.
-\end{minipage}}
 

### 2019-06-18 article.tex
ref TBD.

@@
 \usepackage{booktabs}
+\usepackage{textcomp}
 \usepackage{graphicx}
@@
 Similarly, to the VQE algorithm, one must ensure that the system is prepared in an initial state, but with the exception that the state must have a sufficient overlap with the ground state.
-Once the state is prepared in our desired state, an approximation is applied to the operator.
+Once the state is prepared in our desired state, an approximation is applied to the phase of the operator.
+The operator $U = e^{-iHt}$ enables the initial state $\ket{\psi(0)}$ to change over time to the state $e^{-iEt}\ket{\psi(0)}$.
 Consequently, the initial state is mapped onto a superposition state of various qubits, which is called the ancilla qubits.
@@
 The system as a result collapses to a single state with an associated probability.
-We repeat this algorithm for a higher number of ‘special’ qubits until the lowest eigenenergy is obtained, or more precisely the energy of the ground state.
+We repeat this algorithm for a higher number of ancilla qubits \cite[p.2]{tansuwannont2015quantum} until the lowest eigenenergy is obtained, or more precisely the energy of the ground state.
 
@@
  \centerline{\textbf{PEA}}
- The molecular energies can be obtained by the time evolution of molecular Hamiltonian, which is a unitary operator $U = e^{-iHt}$.
-We can first prepare an initial state that strongly overlaps the ground state of molecular hydrogen.
+ The molecular energies can be obtained by the time evolution of molecular Hamiltonian.
 As any state $\ket{\psi(t)}$ evolved by unitary $U$ can be represent by applying phase difference onto initial state $e^{-iEt}\ket{\psi(0)}$.
@@
 
-Late last year the US passed the new National Quantum Initiative Act pledging around \$1.2 billion in funding for quantum information science.
+Late last year the US passed the new National Quantum Initiative Act pledging around \textdollar1.2 billion in funding for quantum information science \cite{usbill}.
 At a similar time the EU commission launched the €1 billion Quantum Technologies Flagship which will fund over 5000 of the top European researchers in quantum technologies over the next decade.

### 2019-06-18 article.tex
twist box struc and ref finished.

@@
 \usepackage{amsthm}
-\usepackage{booktabs}
+%\usepackage{booktabs}
 \usepackage{textcomp}
@@
 
-\usepackage{listings}
+%\usepackage{listings}
 
@@
 
-This process is repeated a number of times until the estimate energy approaches a specific value. The final result is an approximation the smallest eigenenergy.
+This process is repeated a number of times until the estimate energy approaches a specific value. The final result is an approximation the smallest eigenenergy.\\
+
+\noindent
+\fbox{\begin{minipage}[c]{32em}%
+ \centerline{\textbf{VQE}}
+In 2014, the VQE algorithm was created by Alberto Peruzzo and Jarrod McClean.
+VQE comprises of classical and quantum features making it possible to use both classical and quantum resources to determine solutions to problems that are difficult to solve using a classical computer.
+The flow chart indicates the key instructions of implementing the VQE algorithm.
+The steps are explained in further detail as follows:
+
+\begin{enumerate}
+\item Preparation: Prepare the initial state of the system in terms of the variable theta by applying a quantum circuit.
+Implementing the unitary coupled cluster (UCC) method enables the algorithm to predict the ground state.
+\item Measurement: Measure each local Hamiltonian, $H_{gamma}$  and its corresponding scalar $g_{gamma}$ to find the average value of the Hamiltonian (see Eq. 1 in [article number]).
+\item Minimisation: Use a classical tool to find new solutions of theta in order to find the minimum eigenenergy of the Hamiltonian.
+\item Repetition: By feeding the settings for theta(vector) into the classical minimisation routine, the new settings for a new parameter of theta(vector) i.e.
+theta(vector)’.
+This process is repeated for n iterations until the parameter converges towards to specific value; this will enable an ideal state of the system to be obtained.
+From this, one can deduce a particular value for $E_{0}$, the smallest energy eigenvalue.
+\end{enumerate}
+ \end{minipage}}
 
@@
 The system as a result collapses to a single state with an associated probability.
-We repeat this algorithm for a higher number of ancilla qubits \cite[p.2]{tansuwannont2015quantum} until the lowest eigenenergy is obtained, or more precisely the energy of the ground state.
+We repeat this algorithm for a higher number of ancilla qubits \cite[p.2]{tansuwannont2015quantum} until the lowest eigenenergy is obtained, or more precisely the energy of the ground state.\\
 
+\noindent
 \fbox{\begin{minipage}[c]{32em}%
@@
 \end{minipage}}
+\\
 
+\noindent
 \fbox{\begin{minipage}[c]{32em}%
@@
 Late last year the US passed the new National Quantum Initiative Act pledging around \textdollar1.2 billion in funding for quantum information science \cite{usbill}.
-At a similar time the EU commission launched the €1 billion Quantum Technologies Flagship which will fund over 5000 of the top European researchers in quantum technologies over the next decade.
-In the UK, the EPSRC-backed Quantum Technology Hubs represent part of a £270 million investment to create national networks of quantum expertise.
+At a similar time the EU commission launched the €1 billion Quantum Technologies Flagship which will fund over 5000 of the top European researchers in quantum technologies over the next decade \cite{eubill}.
+In the UK, the EPSRC-backed Quantum Technology Hubs represent part of a £270 million investment to create national networks of quantum expertise \cite{ukbill}.
 With this extraordinary push of late across Europe and also in the US and China, aiming to fast-track quantum technologies out of university research groups and into industrial applications, the importance of this work in quantum chemistry simulations cannot be overstated.
@@
 
-\section{Technical Boxes}
-\section{VQE}
-\section{PEA}
-
-\section{Experimental realisation (SQUID)}
-
 \bibliography{ref}

### 2019-06-18 article.tex
feynman words 40 yrs ago

@@
 \section{Introduction}
-Richard Feynman’s words are as true today as when he spoke them: “Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical, and by golly it's a wonderful problem, because it doesn't look so easy.”
+Richard Feynman’s words are as true today as when he spoke them almost forty years ago: “Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical, and by golly it's a wonderful problem, because it doesn't look so easy.”
 

### 2019-06-18 article.tex
minor ref.

--- 2019-06-18 article.tex
@@
 Thus, we first need to prepare an initial state of the system (think of how you prepared the cup for the coffee following boiling water to be poured in).
-This is done by representing the state in a chosen vector v­­­­0.
+This is done by representing the state in a chosen vector $v_0$.
 The vectors chosen are trial solution (ansatz) since solutions are not chosen in reference to any specific value as such.
@@
 The method utilised predicts the ground state, the lowest possible energy level of an atom.
-The value of the variable and estimate energy are then fed through a programme; this proposes settings for a new variable – let us call this variable v­­­­1.
+The value of the variable and estimate energy are then fed through a programme; this proposes settings for a new variable – let us call this variable $v_1$­.
 Comparing to our coffee example, it has been decided that either a new blend of coffee is necessary as the current coffee might be perhaps too strong!
@@
 Implementing the unitary coupled cluster (UCC) method enables the algorithm to predict the ground state.
-\item Measurement: Measure each local Hamiltonian, $H_{gamma}$  and its corresponding scalar $g_{gamma}$ to find the average value of the Hamiltonian (see Eq. 1 in [article number]).
+\item Measurement: Measure each local Hamiltonian, $H_{gamma}$  and its corresponding scalar $g_{gamma}$ to find the average value of the Hamiltonian \cite[p.2]{o2016scalable}.
 \item Minimisation: Use a classical tool to find new solutions of theta in order to find the minimum eigenenergy of the Hamiltonian.

### 2019-06-18 article.tex

--- 2019-06-18 article.tex
@@
 \subsection{The VQE Algorithm}
+
 Before we run our algorithm, it is imperative to understand that in quantum mechanics, the properties of a system are characterised by a state.
 Thus, we first need to prepare an initial state of the system (think of how you prepared the cup for the coffee following boiling water to be poured in).
-This is done by representing the state in a chosen vector v­­­­0.
+This is done by representing the state in a chosen vector $v_0$.
 The vectors chosen are trial solution (ansatz) since solutions are not chosen in reference to any specific value as such.
@@
 Implementing the unitary coupled cluster (UCC) method enables the algorithm to predict the ground state.
-\item Measurement: Measure each local Hamiltonian, $H_{gamma}$  and its corresponding scalar $g_{gamma}$ to find the average value of the Hamiltonian (see Eq. 1 in [article number]).
+\item Measurement: Measure each local Hamiltonian, $H_{\gamma}$  and its corresponding scalar $g_{\gamma}$ to find the average value of the Hamiltonian \cite[p.2]{o2016scalable}.
 \item Minimisation: Use a classical tool to find new solutions of theta in order to find the minimum eigenenergy of the Hamiltonian.
-\item Repetition: By feeding the settings for theta(vector) into the classical minimisation routine, the new settings for a new parameter of theta(vector) i.e.
-theta(vector)’.
+\item Repetition: By feeding the settings for $\vec{\theta}$ into the classical minimisation routine, the new settings for a new parameter of $\vec{\theta}$ i.e.
+$\vec{\theta}^{\prime}$.
 This process is repeated for n iterations until the parameter converges towards to specific value; this will enable an ideal state of the system to be obtained.

### 2019-06-18 article.tex
fix euro sym.
Fix box width.

@@
 %\usepackage{booktabs}
-\usepackage{textcomp}
+\usepackage{lmodern,textcomp}
 \usepackage{graphicx}
@@
 \noindent
-\fbox{\begin{minipage}[c]{32em}%
+\setlength{\fboxsep}{0.5em}
+\fbox{\begin{minipage}[c]{31em}%
  \centerline{\textbf{VQE}}
@@
 Once the state is prepared in our desired state, an approximation is applied to the phase of the operator.
-The operator $U = e^{-iHt}$ enables the initial state $\ket{\psi(0)}$ to change over time to the state $e^{-iEt}\ket{\psi(0)}$.
+The operator $\hat{U} = e^{-iHt}$ enables the initial state $\ket{\psi(0)}$ to change over time to the state $e^{-iEt}\ket{\psi(0)}$.
 Consequently, the initial state is mapped onto a superposition state of various qubits, which is called the ancilla qubits.
@@
 
-\noindent
-\fbox{\begin{minipage}[c]{32em}%
+\noindent\setlength{\fboxsep}{0.5em}
+\fbox{\begin{minipage}[c]{31em}%
 \centerline{\textbf{PEA}}
 The molecular energies can be obtained by the time evolution of molecular Hamiltonian.
-As any state $\ket{\psi(t)}$ evolved by unitary $U$ can be represent by applying phase difference onto initial state $e^{-iEt}\ket{\psi(0)}$.
+As any state $\ket{\psi(t)}$ evolved by unitary can be represent by applying phase difference onto initial state $e^{-iEt}\ket{\psi(0)}$.
 Phase estimation algorithm (PEA) is used then to find this relative phase and convert it into energy.
@@
 Since we can evolve states by unity operator.
-By inputting both parts of qubits onto a multiple controlled-U gate, the eigenvalue of each unitary $U$ will transform to each one of qubits in first part.
+By inputting both parts of qubits onto a multiple controlled-U gate, the eigenvalue of each unitary $\hat{U}$ will transform to each one of qubits in first part.
 
@@
 
-\noindent
-\fbox{\begin{minipage}[c]{32em}%
+\noindent\setlength{\fboxsep}{0.5em}
+\fbox{\begin{minipage}[c]{31em}%
 \centerline{\textbf{Experimental realisation (SQUID)}}

### 2019-06-19 article.tex
Non-technical section on experimental implementation

@@
 
+\subsection{The Experimental Implementation}
+
+The most widely accepted prerequisites to build a viable physical quantum computing technology were proposed by the American physicist
+David DiVincenzo in 2000, with a few additional conditions added since. The original five DiVincenzo Criteria are:
+
+\begin{enumerate}
+\item Scalable physical system of well-characterised qubits.
+\item Ability to initialize the state of the qubits to a simple fiducial state.
+\item Long decoherence times, much longer than the “gate-operation” time.
+\item Universal set of quantum gates.
+\item Qubit-specific measurement capability.
+\end{enumerate}
+
+Now there are a number of different approaches to building physical quantum computing hardware being pursued by various research groups
+and companies, each with their own pros and cons. Some of the types of implemented qubits include trapped ions, nitrogen-vacancy centres,
+ quantum silicon photonics and superconducting, to name but a few. The type used here is the Xmon transmon qubit, a superconducting qubit
+  built around a superconducting quantum interference device, or SQUID. Variations of the superconducting qubit are being developed by
+  companies such as D-wave, IBM and Rigetti in the current race for quantum supremacy.
+
 \noindent\setlength{\fboxsep}{0.5em}

### 2019-06-19 article.tex
edits to introduction

@@
 \section{Introduction}
-Richard Feynman’s words are as true today as when he spoke them almost forty years ago: “Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical, and by golly it's a wonderful problem, because it doesn't look so easy.”
+“Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical, and by golly it's a wonderful
+ problem, because it doesn't look so easy.” Richard Feynman’s words are as true today as when he spoke them almost forty years ago.
 
-Simulation of physical systems is one of the most crucial practical applications of computation by far.
-On the macroscopic scale of our lives, for instance, buildings are engineered safe and cost efficient using ﬁnite element analysis and modeling.
-Aeronautics rely hugely on computational ﬂuid dynamics simulations.
-Even nuclear weapons are tested by exhaustive computational modeling.
+Simulation of physical systems is one of the most crucial practical applications of computation by far.  For example, buildings are engineered in a safe
+and cost efficient way though the application of ﬁnite element analysis and modeling. The field of aeronautics relies heavily on computational ﬂuid
+dynamics simulations. And even nuclear weapons systems are tested by exhaustive computational modeling.
 
-But even so, classical computation still has its limits, including cost and accuracy.
-Additionally, when it comes to simulating microscopic systems, classical technique also exhibits its downside on efficiency.
-In computational chemistry, each subatomic orbitals and their interactions needs to be considered to achieve an accurate and realistic simulation of the microscopic system.
-Since the state of one orbital can be affected by all of the others, an exponential number of states in the basis of molecular orbitals should be computed.
-This is what we call ‘many body’ problems.
-No matter how far apart two orbitals are, their quantum states cannot be described independently, the repeated interactions between particles create quantum correlations, I.e., entanglement.
+However, even in light of it's phenomenally far-reaching success in almost all areas of modern science and engineering, classical computation still
+has its limitations. When it comes to simulating microscopic systems, classical techniques require significant computational overhead which scales to
+unreasonable proportions with increasing system size. In quantum computational chemistry simulations, each subatomic orbital and their interactions
+needs to be considered to achieve an accurate and realistic simulation of the microscopic system. Since the state of one orbital can be affected by
+all of the others, an exponential number of states in the basis of molecular orbitals needs to be accounted for. This is what we call ‘many body’ problems.
+No matter how far apart two orbitals are, their quantum states cannot be described independently, the repeated interactions between particles create
+quantum correlations, this phenomenon is known as entanglement.
 
-A more advanced computation technique is then employed, quantum computation.
-It harnesses the principles of quantum mechanics, hence solves the classically intractable problems more accurately, faster, with a fine-grained simulation.
+A radically different computing paradigm is then employed to combat this problem, that is quantum computation. It harnesses the principles of quantum
+mechanics, hence solves these classically intractable problems of simulation more accurately, faster, with a more fine-grained simulation.
 
-For those information in our classical computers enough to fill up the entire memory, instead, a quantum computer can only use a few quantum bits, or qubits to store them \cite{trabesinger2012quantum}.
-since the classical storage unit ‘bit’ is binary system base on 0 and 1, but quantum computer encode them into two distinguishable quantum states, and one qubit can represent multiple states once by quantum phenomenon ‘superposition’.
-similarly, if we perform a searching algorithm on a classical string, the enumerate steps would be the number of bits within this string.
-comparably, our processing step will reduce a lot more as we only need to compute once in a quantum processor.
+The amount of information needed to describe interactions in quantum system would quickly fill up the memory in a classical computer, instead,
+a quantum computer can do tasks of this nature efficiently through the use of quantum bits, or qubits to store them \cite{trabesinger2012quantum}.
+Since the classical storage unit ‘bit’ is binary system base on 0 and 1, but quantum computer encode them into two distinguishable quantum states,
+ and one qubit can represent multiple states once by quantum phenomenon ‘superposition’. Similarly, if we perform a searching algorithm on a classical
+ string, the enumerate steps would be the number of bits within this string. Comparably, our processing step will reduce a lot more as we only need to
+  compute once in a quantum processor.
 
 \section{History}
-Molecules consist of various atoms and the elementary unit of an atom is electron and nucleus.
-When we consider atomic energy, electron-nuclei, electron-electron interactions must be examined.
-Molecular energy consists of interactions between multiple atoms, including interactions between electrons from different atoms, as well as nuclei.
-Molecular energy can be pictured as a large package that contains many small balls, and the sum of the energy of their collisions is the sum of interactions between atoms.
+Molecules consist of various atoms and the elementary unit of an atom is electron and nucleus. When we consider atomic energy, electron-nuclei,
+electron-electron interactions must be examined. Molecular energy consists of interactions between multiple atoms, including interactions between
+ electrons from different atoms, as well as nuclei. Molecular energy can be pictured as a large package that contains many small balls, and the
+ sum of the energy of their collisions is the sum of interactions between atoms.
 
-Obviously, it demands massive computation to find out the package energy as it contains a huge amount of particles.
-Therefore, some approximations need to be made to simply our model, hence molecular mechanics is introduced.
+Obviously, it demands massive computation to find out the package energy as it contains a huge amount of particles. Therefore, some approximations
+ need to be made to simply our model, hence molecular mechanics is introduced.
 
-Molecular mechanics models molecular systems using force fields in classical mechanics.
-Three approximations were made to reduce the computational complexity.
-Each atom simulated as one particle; each particle has their designated attributes including radius, Polaris ability and a net charge; and international are treated as springs with an equilibrium distance same as bond length.
-This theory essentially simulated every element of the molecular system as fixed particles connected by strings, which largely reduces the computational complexity.
+Molecular mechanics models molecular systems using force fields in classical mechanics. Three approximations were made to reduce the computational
+ complexity. Each atom simulated as one particle; each particle has their designated attributes including radius, Polaris ability and a net charge;
+  and international are treated as springs with an equilibrium distance same as bond length. This theory essentially simulated every element of the
+   molecular system as fixed particles connected by strings, which largely reduces the computational complexity.
 
-A similar theory of reducing the amount of computation is called renormalisation group.
-A simple scenario is to calculate the resistance force of an iron ball in a glass of water.
-We can simply simulate every water molecule in the glass by inputting the real size of a single water molecule as one parameter.
-The sizes of the molecules can easily be another 1000 parameters as they can be quite irregular and difficult to describe.
-Forces from multiple directions of the iron ball could be another 1000 parameters.
-Inputting all parameters, modelling an iron ball and simulating $10^{26}$ water molecules and their interactions can give the resistance force.
-Let’s say we have a supercomputer that allows tremendous amount of data processing and the result that this simulation gives coincides with experimental data perfectly.
+A similar theory of reducing the amount of computation is called renormalisation group. A simple scenario is to calculate the resistance force of an
+ iron ball in a glass of water. We can simply simulate every water molecule in the glass by inputting the real size of a single water molecule as one
+  parameter. The sizes of the molecules can easily be another 1000 parameters as they can be quite irregular and difficult to describe. Forces from
+  multiple directions of the iron ball could be another 1000 parameters. Inputting all parameters, modelling an iron ball and simulating $10^{26}$
+  water molecules and their interactions can give the resistance force. Let’s say we have a supercomputer that allows tremendous amount of data
+  processing and the result that this simulation gives coincides with experimental data perfectly.
 
-But what if we want to reduce the computational complexity?
-One solution is to reduce the number of water molecule simulated, which is feasible given the relative bigger size of the iron ball.
-To make up for the loss in number of molecules, the rest parameters can be changed.
-Let’s say we manipulated the parameters and the simulation gives slightly different solutions, but the overall trend is still the same as before.
+But what if we want to reduce the computational complexity? One solution is to reduce the number of water molecule simulated, which is feasible given
+ the relative bigger size of the iron ball. To make up for the loss in number of molecules, the rest parameters can be changed. Let’s say we
+ manipulated the parameters and the simulation gives slightly different solutions, but the overall trend is still the same as before.
 
-The computation complexity can still be compressed. We can repeat the process of reducing the number of molecules and adjusting the parameters, and still generate acceptable solutions.
+The computation complexity can still be compressed. We can repeat the process of reducing the number of molecules and adjusting the parameters,
+ and still generate acceptable solutions.
 
-This process is called renormalisation group, and the results that this model generates is called low energy effective theory, in which the system size is reduced but the results is still acceptable and effective.
+This process is called renormalisation group, and the results that this model generates is called low energy effective theory, in which the system
+ size is reduced but the results is still acceptable and effective.
 
-We now return to the theory of molecular mechanics, it is not exactly accurate since it is restricted by parameters of equations, ie difference force fields for different atoms.
-A similar and perhaps more comprehensible explanation can be made from the theory of renormalisation group.
-While decreasing the parameters of calculation and reducing computation time, the accuracy of the result is decreasing as well.
-Molecular mechanics does the same for force fields and interactions inside the atom.
+We now return to the theory of molecular mechanics, it is not exactly accurate since it is restricted by parameters of equations, ie difference
+force fields for different atoms. A similar and perhaps more comprehensible explanation can be made from the theory of renormalisation group.
+While decreasing the parameters of calculation and reducing computation time, the accuracy of the result is decreasing as well. Molecular mechanics
+ does the same for force fields and interactions inside the atom.
 
-Overall, the work on simulation molecular energies with classical methods is a trade off between precision and cost.
-Quantum simulation is able to contain all information relevant to the system and simulate them exactly as reality without approximations.
+Overall, the work on simulation molecular energies with classical methods is a trade off between precision and cost. Quantum simulation is able
+to contain all information relevant to the system and simulate them exactly as reality without approximations.
 
 \section{Non-technical background}
-In any quantum computing processes, the building blocks of the process are qubits.
-A qubit, or quantum bit, is the quantum analogue of the classical bit (strings of zeros and ones).
-So the qubit represents a quantum superposition or combination of a predetermined ‘0’ and a ‘1’ state.
-The quantum algorithms were run on superconducting qubits, these are a physical realisation of quantum bits based upon what are known as superconducting interference devices (SQUIDs), and attempt to find properties of the wavefunction of the molecule (in this case molecular Hydrogen).
+In any quantum computing processes, the building blocks of the process are qubits. A qubit, or quantum bit, is the quantum analogue of the classical
+ bit (strings of zeros and ones). So the qubit represents a quantum superposition or combination of a predetermined ‘0’ and a ‘1’ state. The quantum
+  algorithms were run on superconducting qubits, these are a physical realisation of quantum bits based upon what are known as superconducting
+  interference devices (SQUIDs), and attempt to find properties of the wavefunction of the molecule (in this case molecular Hydrogen).
 
-The wavefunction of a quantum system is a mathematical construct describing the state, it provides probabilities for results of particular measurements made on the state.
-In quantum chemistry the electronic structure of a molecule is described by the movement of the electrons of a collection of fixed atomic nuclei.
-And so a comprehensive description of the electronic structure encompasses the wavefunctions of all of these electrons, along with their respective energies.
-The idea that the motions of the electrons and nuclei may be considered separately is known as the Born-Oppenheimer approximation.
-It is a very useful assumption that simplifies electronic structure calculations appreciably.
+The wavefunction of a quantum system is a mathematical construct describing the state, it provides probabilities for results of particular measurements
+ made on the state. In quantum chemistry the electronic structure of a molecule is described by the movement of the electrons of a collection of fixed
+  atomic nuclei. And so a comprehensive description of the electronic structure encompasses the wavefunctions of all of these electrons, along with
+  their respective energies. The idea that the motions of the electrons and nuclei may be considered separately is known as the Born-Oppenheimer
+  approximation. It is a very useful assumption that simplifies electronic structure calculations appreciably.
 
-One of the reasons that developing new approaches to tackling electronic structure calculations are of importance is that they are extremely computationally expensive.
-Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems in nature by using quantum systems.
-A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum hardware and software that will allow for efficient quantum simulations of chemical systems.
-A problem of tantamount importance in quantum chemistry is that of finding the lowest energy eigenvalue of molecular electronic structures.
-These energy eigenvalues define a great deal of properties of interest in the molecule.
-This is of great interest in for example the development of pharmaceuticals where companies have an extremely laborious testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings and would better ensure that the pharmaceutical under development behaved as required prior to starting trials.
+One of the reasons that developing new approaches to tackling electronic structure calculations are of importance is that they are extremely
+computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems
+ in nature by using quantum systems. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum
+  hardware and software that will allow for efficient quantum simulations of chemical systems. A problem of tantamount importance in quantum chemistry
+  is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy eigenvalues define a great deal of properties of
+  interest in the molecule. This is of great interest in for example the development of pharmaceuticals where companies have an extremely laborious
+  testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings
+  and would better ensure that the pharmaceutical under development behaved as required prior to starting trials.
 \section{Techniques in paper}
@@
 Before we run our algorithm, it is imperative to understand that in quantum mechanics, the properties of a system are characterised by a state.
-Thus, we first need to prepare an initial state of the system (think of how you prepared the cup for the coffee following boiling water to be poured in).
-This is done by representing the state in a chosen vector $v_0$.
-The vectors chosen are trial solution (ansatz) since solutions are not chosen in reference to any specific value as such.
+Thus, we first need to prepare an initial state of the system (think of how you prepared the cup for the coffee following boiling water to be
+poured in). This is done by representing the state in a chosen vector $v_0$. The vectors chosen are trial solution (ansatz) since solutions are
+ not chosen in reference to any specific value as such.
 
 Once a variable is selected, we can find an estimate value of the energy corresponding to the chosen variable by measuring the average energy.
-The method utilised predicts the ground state, the lowest possible energy level of an atom.
-The value of the variable and estimate energy are then fed through a programme; this proposes settings for a new variable – let us call this variable $v_1$­.
-Comparing to our coffee example, it has been decided that either a new blend of coffee is necessary as the current coffee might be perhaps too strong!
+The method utilised predicts the ground state, the lowest possible energy level of an atom. The value of the variable and estimate energy are
+then fed through a programme; this proposes settings for a new variable – let us call this variable $v_1$­. Comparing to our coffee example, it
+ has been decided that either a new blend of coffee is necessary as the current coffee might be perhaps too strong!
 
-This process is repeated a number of times until the estimate energy approaches a specific value. The final result is an approximation the smallest eigenenergy.\\
+This process is repeated a number of times until the estimate energy approaches a specific value. The final result is an approximation the
+smallest eigenenergy.\\
 
@@
  \centerline{\textbf{VQE}}
-In 2014, the VQE algorithm was created by Alberto Peruzzo and Jarrod McClean.
-VQE comprises of classical and quantum features making it possible to use both classical and quantum resources to determine solutions to problems that are difficult to solve using a classical computer.
-The flow chart indicates the key instructions of implementing the VQE algorithm.
-The steps are explained in further detail as follows:
+In 2014, the VQE algorithm was created by Alberto Peruzzo and Jarrod McClean. VQE comprises of classical and quantum features making it possible
+ to use both classical and quantum resources to determine solutions to problems that are difficult to solve using a classical computer. The flow
+ chart indicates the key instructions of implementing the VQE algorithm. The steps are explained in further detail as follows:
 
@@
 \subsection{The Quantum Phase Estimation Algorithm (PEA)}
-Similarly, to the VQE algorithm, one must ensure that the system is prepared in an initial state, but with the exception that the state must have a sufficient overlap with the ground state.
-Once the state is prepared in our desired state, an approximation is applied to the phase of the operator.
-The operator $\hat{U} = e^{-iHt}$ enables the initial state $\ket{\psi(0)}$ to change over time to the state $e^{-iEt}\ket{\psi(0)}$.
-Consequently, the initial state is mapped onto a superposition state of various qubits, which is called the ancilla qubits.
-After that, the state is acted on in turn inducing a phase on the system.
-Since the way in which the system evolves is controlled, it is now entangled with the initialised state.
-Next, we measure the phase obtained corresponding to each value of energy.
-The system as a result collapses to a single state with an associated probability.
-We repeat this algorithm for a higher number of ancilla qubits \cite[p.2]{tansuwannont2015quantum} until the lowest eigenenergy is obtained, or more precisely the energy of the ground state.\\
+Similarly, to the VQE algorithm, one must ensure that the system is prepared in an initial state, but with the exception that the state must have a
+ sufficient overlap with the ground state. Once the state is prepared in our desired state, an approximation is applied to the phase of the operator.
+  The operator $\hat{U} = e^{-iHt}$ enables the initial state $\ket{\psi(0)}$ to change over time to the state $e^{-iEt}\ket{\psi(0)}$. Consequently,
+  the initial state is mapped onto a superposition state of various qubits, which is called the ancilla qubits. After that, the state is acted on in
+  turn inducing a phase on the system. Since the way in which the system evolves is controlled, it is now entangled with the initialised state.
+ Next, we measure the phase obtained corresponding to each value of energy. The system as a result collapses to a single state with an associated
+ probability. We repeat this algorithm for a higher number of ancilla qubits \cite[p.2]{tansuwannont2015quantum} until the lowest eigenenergy is
+  obtained, or more precisely the energy of the ground state.\\
 
@@
 \centerline{\textbf{PEA}}
-The molecular energies can be obtained by the time evolution of molecular Hamiltonian.
-As any state $\ket{\psi(t)}$ evolved by unitary can be represent by applying phase difference onto initial state $e^{-iEt}\ket{\psi(0)}$.
-Phase estimation algorithm (PEA) is used then to find this relative phase and convert it into energy.
-In order to preform PEA we need to prepare two parts of qubits.
-First n qubits of superposition state $\frac{\ket{0} + \ket{1}}{\sqrt 2}$, second, our initial state.
-Since we can evolve states by unity operator.
-By inputting both parts of qubits onto a multiple controlled-U gate, the eigenvalue of each unitary $\hat{U}$ will transform to each one of qubits in first part.
+The molecular energies can be obtained by the time evolution of molecular Hamiltonian. As any state $\ket{\psi(t)}$ evolved by unitary can be represent
+ by applying phase difference onto initial state $e^{-iEt}\ket{\psi(0)}$. Phase estimation algorithm (PEA) is used then to find this relative phase and
+  convert it into energy. In order to preform PEA we need to prepare two parts of qubits. First n qubits of superposition state
+   $\frac{\ket{0} + \ket{1}}{\sqrt 2}$, second, our initial state. Since we can evolve states by unity operator. By inputting both parts of qubits
+   onto a multiple controlled-U gate, the eigenvalue of each unitary $\hat{U}$ will transform to each one of qubits in first part.
 
@@
 \centerline{\textbf{Experimental realisation (SQUID)}}
-The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of superconducting interference device or SQUID.
-It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are charge states, and the superposition of these charge states is tuned using microwave resonators.
-The Xmon qubit has a number of favourable features, which include easy fabrication, fast qubit control and long qubit coherence times.
+The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of
+superconducting interference device or SQUID. It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are
+ charge states, and the superposition of these charge states is tuned using microwave resonators. The Xmon qubit has a number of favourable features,
+  which include easy fabrication, fast qubit control and long qubit coherence times.
 
-Using superconducting qubits is an appealing option for quantum hardware because it provides the scalability which is lacking for some other types of qubit.
-This is on account of the fact that for superconductivity the conduction electrons condense to a macroscopic quantum state which facilitates the creation of large integrated quantum circuits.
+Using superconducting qubits is an appealing option for quantum hardware because it provides the scalability which is lacking for some other types
+of qubit. This is on account of the fact that for superconductivity the conduction electrons condense to a macroscopic quantum state which facilitates
+ the creation of large integrated quantum circuits.
 
-The Xmon qubits are placed inside a dilution refrigerator which is at a temperature of 20mK.
-The inter-qubit coupling, and qubit measurement and control, are all done using microwave resonators.
-Single (or local) quantum gates are achieved using pulses of microwave radiation.
-The entanglement operation used is the controlled-Z or CZ gate, this is achieved by fixing the frequency of one qubit while adiabatically tuning the other qubit from the $\ket{11}$ state to near to the $\ket{02}$  state, which gives a relative phase shift.
-\end{minipage}}
+The Xmon qubits are placed inside a dilution refrigerator which is at a temperature of 20mK. The inter-qubit coupling, and qubit measurement and
+control, are all done using microwave resonators. Single (or local) quantum gates are achieved using pulses of microwave radiation. The entanglement
+ operation used is the controlled-Z or CZ gate, this is achieved by fixing the frequency of one qubit while adiabatically tuning the other qubit
+ from the $\ket{11}$ state to near to the $\ket{02}$  state, which gives a relative phase shift. \end{minipage}}
 
 \section{Main Achievement of paper}
-As it is known, building a quantum computer comes with many challenges, one being the aspect of scalability.
-One of the advantages of using PEA to compute electronic structures of a molecule is better asymptotic scaling which would prove useful for larger molecules than Hydrogen.
-However, this is problematic as one would need to utilise more steps in the Trotterisation approximation which would in turn incur higher exponential costs.
-Hence, it was determined that a single Trotter step is not enough to accurately predict chemical rates for a Hydrogen molecule.
-In addition, for a single trotter step, each simulation using PEA was ran using different orderings of local Hamiltonians in order to find the optimal Trotter sequence for each bond length.
-For larger molecules, this is deemed intractable which becomes extremely difficult for the preprocessing requirements for a classical computer.
+As it is known, building a quantum computer comes with many challenges, one being the aspect of scalability. One of the advantages of using PEA to
+compute electronic structures of a molecule is better asymptotic scaling which would prove useful for larger molecules than Hydrogen. However, this
+is problematic as one would need to utilise more steps in the Trotterisation approximation which would in turn incur higher exponential costs. Hence,
+ it was determined that a single Trotter step is not enough to accurately predict chemical rates for a Hydrogen molecule. In addition, for a single
+ trotter step, each simulation using PEA was ran using different orderings of local Hamiltonians in order to find the optimal Trotter sequence for
+ each bond length. For larger molecules, this is deemed intractable which becomes extremely difficult for the preprocessing requirements for a
+ classical computer.
 
-On the contrary, VQE was proved to be more effective due to its robustness to error.
-This is due to its success in predicting the chemical dissociation rate below the chemical accuracy threshold.
-Due to its short measurement sequences, it is more viable to use VQE for quantum simulations.
+On the contrary, VQE was proved to be more effective due to its robustness to error. This is due to its success in predicting the chemical dissociation
+ rate below the chemical accuracy threshold. Due to its short measurement sequences, it is more viable to use VQE for quantum simulations.
  Consequently, the quantum coherence of the system would be preserved which would limit the quantum error correction.
 
-Although a quantum simulation such as the VQE is almost foolproof it may still not be adequate to calculate exact numerical solutions that are characteristic of various types of molecules and their interactions.
-Quantum computing shows promise to eliminate such errors whilst using a larger number of qubits.
-However, these factors work against each other.
-If such a machine can be built, there would be more states and thus information to manipulate whilst withstanding error.
-This could revolutionise applications such as pharmaceuticals where cures and treatments for complex or incurable diseases such as Cancer, Prion disease and so forth could be engineered.
-If (or when should I say) this is possible,  we would have a machine taking on the roles of a chemist, problem solver and designer simultaneously and combined into one entity!
+Although a quantum simulation such as the VQE is almost foolproof it may still not be adequate to calculate exact numerical solutions that are
+characteristic of various types of molecules and their interactions. Quantum computing shows promise to eliminate such errors whilst using a
+larger number of qubits. However, these factors work against each other. If such a machine can be built, there would be more states and thus
+information to manipulate whilst withstanding error. This could revolutionise applications such as pharmaceuticals where cures and treatments
+ for complex or incurable diseases such as Cancer, Prion disease and so forth could be engineered. If (or when should I say) this is possible,
+  we would have a machine taking on the roles of a chemist, problem solver and designer simultaneously and combined into one entity!
 \section{Conclusion and outlook}
-As this is the first scalable simulation of molecular energies on any type of quantum hardware it represents an important step in the history of quantum computing applications.
-The results indicate that for near-term quantum devices without effective error correction the adaptive approach represented by the Variational Quantum Eigensolver may have better error resilience than that of standard gate model approach represented by the Phase Estimation Algorithm.
-The expectation is that this work will pave the way for the development of further techniques for intractable calculations in quantum chemistry.
-And the final aim is that eventually these variational quantum chemistry techniques will allow for numerically exact simulations of chemical reaction rates, which are of great industrial commercial value.
-In particular, the efficiency - requiring only short state preparation and measurement procedures, and so it is without the normal substantial overhead required for quantum error correction - and robustness to error displayed by the experimental implementation of the variational quantum eigensolver technique indicates that this technique might succeed where classical techniques fail in solving traditionally intractable problems.
+As this is the first scalable simulation of molecular energies on any type of quantum hardware it represents an important step in the history of
+quantum computing applications. The results indicate that for near-term quantum devices without effective error correction the adaptive approach
+represented by the Variational Quantum Eigensolver may have better error resilience than that of standard gate model approach represented by the
+Phase Estimation Algorithm. The expectation is that this work will pave the way for the development of further techniques for intractable calculations
+ in quantum chemistry. And the final aim is that eventually these variational quantum chemistry techniques will allow for numerically exact simulations
+  of chemical reaction rates, which are of great industrial commercial value. In particular, the efficiency - requiring only short state preparation
+   and measurement procedures, and so it is without the normal substantial overhead required for quantum error correction - and robustness to
+   error displayed by the experimental implementation of the variational quantum eigensolver technique indicates that this technique might succeed
+    where classical techniques fail in solving traditionally intractable problems.
 
-Late last year the US passed the new National Quantum Initiative Act pledging around \textdollar1.2 billion in funding for quantum information science \cite{usbill}.
-At a similar time the EU commission launched the €1 billion Quantum Technologies Flagship which will fund over 5000 of the top European researchers in quantum technologies over the next decade \cite{eubill}.
-In the UK, the EPSRC-backed Quantum Technology Hubs represent part of a £270 million investment to create national networks of quantum expertise \cite{ukbill}.
-With this extraordinary push of late across Europe and also in the US and China, aiming to fast-track quantum technologies out of university research groups and into industrial applications, the importance of this work in quantum chemistry simulations cannot be overstated.
-As aside from the much touted almost pop-science status of quantum encryption, the myriad opportunities afforded by more efficient scalable quantum chemistry simulations looms large in garnering serious investor interest.
-The ability to run quantum simulations of the behaviour of molecules and materials is hoped offer new avenues for increasing our understanding of chemistry and enable the development of new medicines and materials in silico.
+Late last year the US passed the new National Quantum Initiative Act pledging around \textdollar1.2 billion in funding for quantum information science
+ \cite{usbill}. At a similar time the EU commission launched the €1 billion Quantum Technologies Flagship which will fund over 5000 of the top
+ European researchers in quantum technologies over the next decade \cite{eubill}. In the UK, the EPSRC-backed Quantum Technology Hubs represent
+ part of a £270 million investment to create national networks of quantum expertise \cite{ukbill}. With this extraordinary push of late across
+ Europe and also in the US and China, aiming to fast-track quantum technologies out of university research groups and into industrial applications,
+  the importance of this work in quantum chemistry simulations cannot be overstated. As aside from the much touted almost pop-science status of
+  quantum encryption, the myriad opportunities afforded by more efficient scalable quantum chemistry simulations looms large in garnering serious
+   investor interest. The ability to run quantum simulations of the behaviour of molecules and materials is hoped offer new avenues for increasing
+    our understanding of chemistry and enable the development of new medicines and materials in silico.
 

### 2019-06-19 article.tex
further edits to intro

@@
 
-The amount of information needed to describe interactions in quantum system would quickly fill up the memory in a classical computer, instead,
-a quantum computer can do tasks of this nature efficiently through the use of quantum bits, or qubits to store them \cite{trabesinger2012quantum}.
-Since the classical storage unit ‘bit’ is binary system base on 0 and 1, but quantum computer encode them into two distinguishable quantum states,
- and one qubit can represent multiple states once by quantum phenomenon ‘superposition’. Similarly, if we perform a searching algorithm on a classical
- string, the enumerate steps would be the number of bits within this string. Comparably, our processing step will reduce a lot more as we only need to
-  compute once in a quantum processor.
+The amount of information needed to describe interactions in a quantum system would quickly fill up the memory in a classical computer, instead,
+a quantum computer can do tasks of this nature efficiently through the use of quantum bits, or qubits to information storage and computation
+\cite{trabesinger2012quantum}. Since the classical storage unit ‘bit’ is binary system based on strings of 0s and 1s, but quantum computer encodes
+ them into two distinguishable quantum states, and one qubit can represent multiple states once by quantum phenomenon ‘superposition’. Similarly,
+ if we perform a searching algorithm on a classical string, the enumerate steps would be the number of bits within this string. Comparably, our
+ processing step will reduce a lot more as we only need to compute once in a quantum processor.
 

### 2019-06-19 article.tex
further edits to intro

@@
 needs to be considered to achieve an accurate and realistic simulation of the microscopic system. Since the state of one orbital can be affected by
-all of the others, an exponential number of states in the basis of molecular orbitals needs to be accounted for. This is what we call ‘many body’ problems.
-No matter how far apart two orbitals are, their quantum states cannot be described independently, the repeated interactions between particles create
+all of the others, an exponential number of states in the basis of molecular orbitals needs to be accounted for. Problems of this type are classified
+to be ‘many-body’ problems. No matter how far apart two orbitals are, their quantum states cannot be described independently, the repeated interactions between particles create
 quantum correlations, this phenomenon is known as entanglement.
@@
 
-The amount of information needed to describe interactions in a quantum system would quickly fill up the memory in a classical computer, instead,
-a quantum computer can do tasks of this nature efficiently through the use of quantum bits, or qubits to information storage and computation
-\cite{trabesinger2012quantum}. Since the classical storage unit ‘bit’ is binary system based on strings of 0s and 1s, but quantum computer encodes
- them into two distinguishable quantum states, and one qubit can represent multiple states once by quantum phenomenon ‘superposition’. Similarly,
- if we perform a searching algorithm on a classical string, the enumerate steps would be the number of bits within this string. Comparably, our
- processing step will reduce a lot more as we only need to compute once in a quantum processor.
+The amount of information needed to describe interactions in a quantum system would quickly fill up the memory of a classical computer, instead,
+a quantum computer can do tasks of this nature efficiently through the use of quantum bits, or qubits, for information storage and computation
+\cite{trabesinger2012quantum}. Since the classical storage unit ‘bit’ is binary system based on strings of 0s and 1s, but a quantum computer would
+encode them into two distinguishable quantum states, and one qubit can represent multiple states at once in the form of the quantum phenomenon of
+‘superposition’. Similarly, if we perform a search algorithm on a classical string, the enumerate steps would be the number of bits within this
+string. Comparably, our processing step will reduce a lot more as we only need to compute once in a quantum processor.
 

### 2019-06-19 article.tex
Finish PEA box.

--- 2019-06-19 article.tex
@@
 
-Now let us recap Quantum Fourier Transformation, one transforms the tensor product of multiple states onto phase of some superposition states.
+Now let us recap Quantum Fourier Transformation, one transforms the tensor product of multiple states onto phase of some superposition states:
 \begin{footnotesize}
 \[
-	\ket{j_{1} j_{2} \cdots j_{n}}\rightarrow \frac{\left(\ket{0}+e^{2 \pi i 0.
+	\ket{j_{1} j_{2} \cdots j_{n}}\rightarrow \frac{\overbrace{\left(\ket{0}+e^{2 \pi i 0.
 j_{n}}\ket{1}\right)\left(\ket{0}+e^{2 \pi i 0.
 j_{n-1} j_{n}}\ket{1}\right) \cdots\left( \ket{0}+e^{2 \pi i 0.
-j_{1} j_{2} \cdots j_{n-1} j_{n} }\ket{1}\right)}{2^{\frac{n}{2}}}
+j_{1} j_{2} \cdots j_{n-1} j_{n} }\ket{1}\right)}^{\text{our prepared superposition qubits}}}{2^{\frac{n}{2}}}.
 \]
 \end{footnotesize}
-
+As we can see, the result of QFT is just the first part of qubits we prepared.
+Therefore we would apply the reverse QFT onto those qubits, and outputs a single state contains all information about phase we want!
 \end{minipage}}
-\\
 
@@
 \centerline{\textbf{Experimental realisation (SQUID)}}
-The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of
-superconducting interference device or SQUID. It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are
- charge states, and the superposition of these charge states is tuned using microwave resonators. The Xmon qubit has a number of favourable features,
-  which include easy fabrication, fast qubit control and long qubit coherence times.
+The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of superconducting interference device or SQUID.
+It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are charge states, and the superposition of these charge states is tuned using microwave resonators.
+The Xmon qubit has a number of favourable features, which include easy fabrication, fast qubit control and long qubit coherence times.
 
-Using superconducting qubits is an appealing option for quantum hardware because it provides the scalability which is lacking for some other types
-of qubit. This is on account of the fact that for superconductivity the conduction electrons condense to a macroscopic quantum state which facilitates
- the creation of large integrated quantum circuits.
+Using superconducting qubits is an appealing option for quantum hardware because it provides the scalability which is lacking for some other types of qubit.
+This is on account of the fact that for superconductivity the conduction electrons condense to a macroscopic quantum state which facilitates the creation of large integrated quantum circuits.
 
-The Xmon qubits are placed inside a dilution refrigerator which is at a temperature of 20mK. The inter-qubit coupling, and qubit measurement and
-control, are all done using microwave resonators. Single (or local) quantum gates are achieved using pulses of microwave radiation. The entanglement
- operation used is the controlled-Z or CZ gate, this is achieved by fixing the frequency of one qubit while adiabatically tuning the other qubit
- from the $\ket{11}$ state to near to the $\ket{02}$  state, which gives a relative phase shift. \end{minipage}}
+The Xmon qubits are placed inside a dilution refrigerator which is at a temperature of 20mK.
+The inter-qubit coupling, and qubit measurement and control, are all done using microwave resonators.
+Single (or local) quantum gates are achieved using pulses of microwave radiation.
+The entanglement operation used is the controlled-Z or CZ gate, this is achieved by fixing the frequency of one qubit while adiabatically tuning the other qubit from the $\ket{11}$ state to near to the $\ket{02}$  state, which gives a relative phase shift.
+\end{minipage}}
 

### 2019-06-19 article.tex
edits to history
Add VQE diagram.

@@
 \section{History}
-Molecules consist of various atoms and the elementary unit of an atom is electron and nucleus. When we consider atomic energy, electron-nuclei,
-electron-electron interactions must be examined. Molecular energy consists of interactions between multiple atoms, including interactions between
- electrons from different atoms, as well as nuclei. Molecular energy can be pictured as a large package that contains many small balls, and the
- sum of the energy of their collisions is the sum of interactions between atoms.
+Molecules are composed of some collection of atoms, and the elementary units of the atom are the electron and the atomic nucleus. When we consider
+ atomic energy, electron-nuclei, electron-electron interactions must be examined. Molecular energy consists of interactions between multiple atoms,
+ including interactions between electrons from different atoms, as well as nuclei. Molecular energy can be pictured as a large package that contains
+ many small balls, and the sum of the energy of their collisions is the sum of interactions between atoms.
 
@@
 
-This process is repeated a number of times until the estimate energy approaches a specific value. The final result is an approximation the
-smallest eigenenergy.\\
+This process is repeated a number of times until the estimate energy approaches a specific value.
+The final result is an approximation the smallest eigenenergy.
+The Figure \ref{VQE} illustrate the key outline of the VQE algorithm.
+\begin{figure}[H]
+\begin{center}
+\includegraphics[scale=0.75]{VQEdiagram.pdf}
+\end{center}
+\caption{VQE flowchart}\label{VQE}
+\end{figure}
 

### 2019-06-19 article.tex
more edits to history

--- 2019-06-19 article.tex
@@
 \section{History}
-Molecules consist of various atoms and the elementary unit of an atom is electron and nucleus. When we consider atomic energy, electron-nuclei,
-electron-electron interactions must be examined. Molecular energy consists of interactions between multiple atoms, including interactions between
- electrons from different atoms, as well as nuclei. Molecular energy can be pictured as a large package that contains many small balls, and the
- sum of the energy of their collisions is the sum of interactions between atoms.
+Molecules are composed of collections of atoms, and the units that make up an atom are electrons and the atomic nucleus. When we consider the
+ atomic energy then we must take into account both electron-nuclei and electron-electron interactions. The molecular energy consists of interactions
+ between multiple atoms, and interactions between electrons from different nuclei. Molecular energy can be pictured as a large
+ package that contains many small balls, and the sum of the energy of their collisions is the sum of interactions between atoms.
 

### 2019-06-20 article.tex
edits to history

@@
 Obviously, it demands massive computation to find out the package energy as it contains a huge amount of particles. Therefore, some approximations
- need to be made to simply our model, hence molecular mechanics is introduced.
+ need to be made to simply our model, which necessitates the introduction of molecular mechanics.
 
 Molecular mechanics models molecular systems using force fields in classical mechanics. Three approximations were made to reduce the computational
- complexity. Each atom simulated as one particle; each particle has their designated attributes including radius, Polaris ability and a net charge;
+ complexity. Each atom is simulated as one particle; each particle has their designated attributes including radius, Polaris ability and net charge;
  and international are treated as springs with an equilibrium distance same as bond length. This theory essentially simulated every element of the
@@
   and would better ensure that the pharmaceutical under development behaved as required prior to starting trials.
+
 \section{Techniques in paper}
-If I asked you how to make a cup of coffee, your response would go a little something like this; prepare a cup (clean of course), put a number of teaspoons of coffee (depends on how strong you like your coffee), boil the kettle, pour the hot water into the cup and lastly stir.
-You have now made your cup of instant coffee by following a set of instructions.
+If I asked you how to make a cup of coffee, your response would go a little something like this; prepare a cup (clean of course), put a number of
+ teaspoons of coffee (depends on how strong you like your coffee), boil the kettle, pour the hot water into the cup and lastly stir. You have now
+ made your cup of instant coffee by following a set of instructions.
 
-Now, imagine that I asked you to compute the energy surface of a given molecule; how would you carry out this task?
-You would execute an algorithm that produces a numerical value.
-In Scalar Quantum of Molecular Energies two techniques used to determine the energy surface for a hydrogen molecule are discussed as follows:
+Now, imagine that I asked you to compute the energy surface of a given molecule; how would you carry out this task? You would execute an algorithm
+ that produces a numerical value. In Scalar Quantum of Molecular Energies two techniques used to determine the energy surface for a hydrogen molecule
+ are discussed as follows:
 \begin{itemize}
@@
 \centerline{\textbf{Experimental realisation (SQUID)}}
-The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of superconducting interference device or SQUID.
-It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are charge states, and the superposition of these charge states is tuned using microwave resonators.
-The Xmon qubit has a number of favourable features, which include easy fabrication, fast qubit control and long qubit coherence times.
+The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of
+superconducting interference device or SQUID. It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are
+charge states, and the superposition of these charge states is tuned using microwave resonators. The Xmon qubit has a number of favourable features,
+ which include easy fabrication, fast qubit control and long qubit coherence times.
 
-Using superconducting qubits is an appealing option for quantum hardware because it provides the scalability which is lacking for some other types of qubit.
-This is on account of the fact that for superconductivity the conduction electrons condense to a macroscopic quantum state which facilitates the creation of large integrated quantum circuits.
+Using superconducting qubits is an appealing option for quantum hardware because it provides the scalability which is lacking for some other types
+ of qubit. This is on account of the fact that for superconductivity the conduction electrons condense to a macroscopic quantum state which
+ facilitates the creation of large integrated quantum circuits.
 
-The Xmon qubits are placed inside a dilution refrigerator which is at a temperature of 20mK.
-The inter-qubit coupling, and qubit measurement and control, are all done using microwave resonators.
-Single (or local) quantum gates are achieved using pulses of microwave radiation.
-The entanglement operation used is the controlled-Z or CZ gate, this is achieved by fixing the frequency of one qubit while adiabatically tuning the other qubit from the $\ket{11}$ state to near to the $\ket{02}$  state, which gives a relative phase shift.
-\end{minipage}}
+The Xmon qubits are placed inside a dilution refrigerator which is at a temperature of 20mK. The inter-qubit coupling, and qubit measurement
+and control, are all done using microwave resonators. Single (or local) quantum gates are achieved using pulses of microwave radiation.
+The entanglement operation used is the controlled-Z or CZ gate, this is achieved by fixing the frequency of one qubit while adiabatically
+tuning the other qubit from the $\ket{11}$ state to near to the $\ket{02}$  state, which gives a relative phase shift. \end{minipage}}
 

### 2019-06-20 article.tex
more edits to history

@@
  complexity. Each atom is simulated as one particle; each particle has their designated attributes including radius, Polaris ability and net charge;
- and international are treated as springs with an equilibrium distance same as bond length. This theory essentially simulated every element of the
- molecular system as fixed particles connected by strings, which largely reduces the computational complexity.
+ and international are treated as springs with an equilibrium distance same as bond length. Essentially this theory simulates every element of the
+ molecular system as if it were fixed particles connected by strings, which hugely reduces the computational complexity.
 
-A similar theory of reducing the amount of computation is called renormalisation group. A simple scenario is to calculate the resistance force of an
- iron ball in a glass of water. We can simply simulate every water molecule in the glass by inputting the real size of a single water molecule as one
-  parameter. The sizes of the molecules can easily be another 1000 parameters as they can be quite irregular and difficult to describe. Forces from
-  multiple directions of the iron ball could be another 1000 parameters. Inputting all parameters, modelling an iron ball and simulating $10^{26}$
-  water molecules and their interactions can give the resistance force. Let’s say we have a supercomputer that allows tremendous amount of data
-  processing and the result that this simulation gives coincides with experimental data perfectly.
+The renormalisation group is a theory which also enables a reduction in the computational power needed for accurate simulations. A simple scenario
+is to calculate the resistance force of an iron ball in a glass of water. We can simply simulate every water molecule in the glass by using the
+ real size of a single water molecule as one parameter - the sizes of the molecules can easily be another 1000 parameters as they can be
+ irregular and difficult to describe. Forces from multiple directions of the iron ball could be another 1000 parameters. Inputting all parameters,
+  modelling an iron ball and simulating $10^{26}$ water molecules and their interactions can give the resistance force. Let’s say we have a
+  supercomputer that allows for a tremendous amount of data processing and the result that this simulation gives coincides with the experimental data
+  to within an extremely high degree of accuracy.
 
-But what if we want to reduce the computational complexity? One solution is to reduce the number of water molecule simulated, which is feasible given
- the relative bigger size of the iron ball. To make up for the loss in number of molecules, the rest parameters can be changed. Let’s say we
- manipulated the parameters and the simulation gives slightly different solutions, but the overall trend is still the same as before.
+But what if we want to reduce the computational complexity? One solution is to reduce the number of water molecules simulated, which is feasible given
+ the relative much larger size of the iron ball. To make up for the loss in number of molecules, the rest if the parameters can be adapted. Whereby we
+can manipulate the parameters and the simulation gives slightly different solutions, but the overall trend is still the same as before.
 
-The computation complexity can still be compressed. We can repeat the process of reducing the number of molecules and adjusting the parameters,
+The computation complexity can still be compressed. We can repeat the process of reducing the number of molecules and adjusting the parameters
  and still generate acceptable solutions.
 
-This process is called renormalisation group, and the results that this model generates is called low energy effective theory, in which the system
- size is reduced but the results is still acceptable and effective.
+This process is known as renormalisation group, and the results that this model generates are called low energy effective theory, in which the system
+ size is reduced but the results are still accurate.
 
-We now return to the theory of molecular mechanics, it is not exactly accurate since it is restricted by parameters of equations, ie difference
+We now return to the theory of molecular mechanics, it is not exactly accurate since it is restricted by parameters of equations, i.e. difference
 force fields for different atoms. A similar and perhaps more comprehensible explanation can be made from the theory of renormalisation group.
@@
 
-Overall, the work on simulation molecular energies with classical methods is a trade off between precision and cost. Quantum simulation is able
-to contain all information relevant to the system and simulate them exactly as reality without approximations.
+Overall, the work on simulating molecular energies with classical methods is a trade off between precision and cost. Quantum simulation is able
+to encapsulate all the relevant information of the system, and can simulate efficiently and without approximations.
 

### 2019-06-20 article.tex
add PEA diagram.

@@
 \begin{center}
-\includegraphics[scale=0.75]{VQEdiagram.pdf}
+\includegraphics[scale=1]{VQEdiagram.pdf}
 \end{center}
@@
  probability. We repeat this algorithm for a higher number of ancilla qubits \cite[p.2]{tansuwannont2015quantum} until the lowest eigenenergy is
-  obtained, or more precisely the energy of the ground state.\\
+  obtained, or more precisely the energy of the ground state.
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[scale=1.1]{PEA.pdf}
+\end{center}
+\caption{PEA flowchart}
+\end{figure}
 
@@
 \centerline{\textbf{PEA}}
-The molecular energies can be obtained by the time evolution of molecular Hamiltonian. As any state $\ket{\psi(t)}$ evolved by unitary can be represent
+The PEA is a quantum subroutine of the original quantum algorithm for chemistry used to computer eigenenergies of a given molecular structure.
+As any state $\ket{\psi(t)}$ evolved by unitary can be represent
  by applying phase difference onto initial state $e^{-iEt}\ket{\psi(0)}$. Phase estimation algorithm (PEA) is used then to find this relative phase and
@@
 As we can see, the result of QFT is just the first part of qubits we prepared.
-Therefore we would apply the reverse QFT onto those qubits, and outputs a single state contains all information about phase we want!
+Therefore we would apply the reverse QFT onto those qubits, and outputs a single state contains all information about phase we want.
+The algorithm then deduces the relative phase and converts it into energy.
 \end{minipage}}

### 2019-06-20 article.tex
updates

--- 2019-06-20 article.tex
@@
  complexity. Each atom is simulated as one particle; each particle has their designated attributes including radius, Polaris ability and net charge;
- and international are treated as springs with an equilibrium distance same as bond length. Essentially this theory simulates every element of the
+ and interactions are treated as springs with an equilibrium distance same as bond length. Essentially this theory simulates every element of the
  molecular system as if it were fixed particles connected by strings, which hugely reduces the computational complexity.
@@
 
-We now return to the theory of molecular mechanics, it is not exactly accurate since it is restricted by parameters of equations, i.e. difference
+We now return to the theory of molecular mechanics, it is not exactly accurate since it is restricted by parameters of equations, i.e. different
 force fields for different atoms. A similar and perhaps more comprehensible explanation can be made from the theory of renormalisation group.
@@
 \section{Non-technical background}
+
 In any quantum computing processes, the building blocks of the process are qubits. A qubit, or quantum bit, is the quantum analogue of the classical
@@
 
-One of the reasons that developing new approaches to tackling electronic structure calculations are of importance is that they are extremely
+One of the reasons that developing new approaches to tackling electronic structure calculations is of importance is that they are extremely
 computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems
- in nature by using quantum systems. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum
+ in nature by using quantum systems. A prominent driving factor of the interest in and development of quantum computing is the aim to create quantum
  hardware and software that will allow for efficient quantum simulations of chemical systems. A problem of tantamount importance in quantum chemistry

### 2019-06-20 article.tex
typo

--- 2019-06-20 article.tex
@@
 Overall, the work on simulating molecular energies with classical methods is a trade off between precision and cost. Quantum simulation is able
-to encapsulate all the relevant information of the system, and can simulate efficiently and without approximations.
+to encapsulate all the relevant information of the system, and can simulate efficiently and with high accuracy.
 
@@
 
-The wavefunction of a quantum system is a mathematical construct describing the state, it provides probabilities for results of particular measurements
+The wavefunction of a quantum system is a mathematical construct describing the state; it provides probabilities for results of particular measurements
  made on the state. In quantum chemistry the electronic structure of a molecule is described by the movement of the electrons of a collection of fixed
-  atomic nuclei. And so a comprehensive description of the electronic structure encompasses the wavefunctions of all of these electrons, along with
+  atomic nuclei. And thus a comprehensive description of the electronic structure encompasses the wavefunctions of all of these electrons, along with
   their respective energies. The idea that the motions of the electrons and nuclei may be considered separately is known as the Born-Oppenheimer
@@
   is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy eigenvalues define a great deal of properties of
-  interest in the molecule. This is of great interest in for example the development of pharmaceuticals where companies have an extremely laborious
+  interest in the molecule. This is of great importance in for example the development of pharmaceuticals where companies have an extremely laborious
   testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings

### 2019-06-20 article.tex

@@
 Overall, the work on simulating molecular energies with classical methods is a trade off between precision and cost. Quantum simulation is able
-to encapsulate all the relevant information of the system, and can simulate efficiently and with high accuracy.
+to encapsulate all the relevant information of the system, and can simulate efficiently and without approximations.
 
 \section{Non-technical background}
+
 In any quantum computing processes, the building blocks of the process are qubits. A qubit, or quantum bit, is the quantum analogue of the classical
@@
 
-One of the reasons that developing new approaches to tackling electronic structure calculations are of importance is that they are extremely
-computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems
- in nature by using quantum systems. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum
+One of the reasons that developing new approaches to tackling electronic structure calculations is of importance is that they are extremely
+computationally expensive.
+Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems in nature by using quantum systems.
+A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum
   hardware and software that will allow for efficient quantum simulations of chemical systems. A problem of tantamount importance in quantum chemistry
@@
 Thus, we first need to prepare an initial state of the system (think of how you prepared the cup for the coffee following boiling water to be
-poured in). This is done by representing the state in a chosen vector $v_0$. The vectors chosen are trial solution (ansatz) since solutions are
+poured in). This is done by representing the state in a chosen vector $v_0$. The vectors chosen are trial solutions (ansatz) since solutions are
  not chosen in reference to any specific value as such.
@@
 Once a variable is selected, we can find an estimate value of the energy corresponding to the chosen variable by measuring the average energy.
-The method utilised predicts the ground state, the lowest possible energy level of an atom. The value of the variable and estimate energy are
+The method utilised predicts the ground state, the lowest possible energy level of an atom. The values of the variable and estimate energy are
 then fed through a programme; this proposes settings for a new variable – let us call this variable $v_1$­. Comparing to our coffee example, it
@@
 This process is repeated a number of times until the estimate energy approaches a specific value.
-The final result is an approximation the smallest eigenenergy.
-The Figure \ref{VQE} illustrate the key outline of the VQE algorithm.
+The final result is an approximation of the smallest eigenenergy.
+Figure \ref{VQE} illustrates the key outline of the VQE algorithm.
 \begin{figure}[H]
@@
  \centerline{\textbf{VQE}}
-In 2014, the VQE algorithm was created by Alberto Peruzzo and Jarrod McClean. VQE comprises of classical and quantum features making it possible
+In 2014, the VQE algorithm was created by Alberto Peruzzo and Jarrod McClean. VQE comprises of classical and quantum features. This makes it possible
  to use both classical and quantum resources to determine solutions to problems that are difficult to solve using a classical computer. The flow
@@
 \begin{enumerate}
-\item Preparation: Prepare the initial state of the system in terms of the variable theta by applying a quantum circuit.
+\item Preparation: Prepare the initial state of the system in terms of the variable $\vec{\theta}$ by applying a quantum circuit.
 Implementing the unitary coupled cluster (UCC) method enables the algorithm to predict the ground state.

### 2019-06-20 article.tex
typo
updates

--- 2019-06-20 article.tex
@@
  between multiple atoms, and interactions between electrons from different nuclei. Molecular energy can be pictured as a large
- package that contains many small balls, and the sum of the energy of their collisions is the sum of interactions between atoms.
-
-Obviously, it demands massive computation to find out the package energy as it contains a huge amount of particles. Therefore, some approximations
- need to be made to simply our model, which necessitates the introduction of molecular mechanics.
+ package that contains many small balls, and the sum of the energy of their collisions is the sum of interactions between atoms. Obviously, it
+ demands massive computation to find out the package energy as it contains a huge amount of particles. Therefore, some approximations need to be
+  made to simply our model, which necessitates the introduction of molecular mechanics.
 
@@
  the relative much larger size of the iron ball. To make up for the loss in number of molecules, the rest if the parameters can be adapted. Whereby we
-can manipulate the parameters and the simulation gives slightly different solutions, but the overall trend is still the same as before.
-
-The computation complexity can still be compressed. We can repeat the process of reducing the number of molecules and adjusting the parameters
- and still generate acceptable solutions.
-
-This process is known as renormalisation group, and the results that this model generates are called low energy effective theory, in which the system
- size is reduced but the results are still accurate.
+can manipulate the parameters and the simulation gives slightly different solutions, but the overall trend is still the same as before. The computation
+ complexity can still be compressed. We can repeat the process of reducing the number of molecules and adjusting the parameters and still generate
+  acceptable solutions. This process is known as renormalisation group, and the results that this model generates are called low energy effective
+  theory, in which the system size is reduced but the results are still accurate.
 
@@
 computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems
- in nature by using quantum systems. A prominent driving factor of the interest in and development of quantum computing is the aim to create quantum
+ in nature by using quantum systems. A primary driving factor of the interest in and development of quantum computing is the aim to create quantum
  hardware and software that will allow for efficient quantum simulations of chemical systems. A problem of tantamount importance in quantum chemistry
  is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy eigenvalues define a great deal of properties of
- interest in the molecule. This is of great interest in for example the development of pharmaceuticals where companies have an extremely laborious
+ interest in the molecule. This is of great importance in for example the development of pharmaceuticals where companies have an extremely laborious
  testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings
@@
   we would have a machine taking on the roles of a chemist, problem solver and designer simultaneously and combined into one entity!
+
 \section{Conclusion and outlook}

### 2019-06-20 article.tex
typo

--- 2019-06-20 article.tex
@@
   The operator $\hat{U} = e^{-iHt}$ enables the initial state $\ket{\psi(0)}$ to change over time to the state $e^{-iEt}\ket{\psi(0)}$. Consequently,
-  the initial state is mapped onto a superposition state of various qubits, which is called the ancilla qubits. After that, the state is acted on in
+  the initial state is mapped onto a superposition state of various qubits, which is called the ancilla qubits. After that, the state is acted on, in
   turn inducing a phase on the system. Since the way in which the system evolves is controlled, it is now entangled with the initialised state.

### 2019-06-21 article.tex
background edits

@@
 
-In any quantum computing processes, the building blocks of the process are qubits. A qubit, or quantum bit, is the quantum analogue of the classical
- bit (strings of zeros and ones). So the qubit represents a quantum superposition or combination of a predetermined ‘0’ and a ‘1’ state. The quantum
-  algorithms were run on superconducting qubits, these are a physical realisation of quantum bits based upon what are known as superconducting
-  interference devices (SQUIDs), and attempt to find properties of the wavefunction of the molecule (in this case molecular Hydrogen).
+The building blocks of any quantum computing process may be considered to be qubits. A qubit, or quantum bit, is the quantum analogue of the
+classical bit in which classical information is encoded in 0s and 1s. So the qubit represents a quantum superposition or simultaneous combination of
+both a predetermined ‘0’ and a ‘1’ state. The quantum algorithms were run on superconducting qubits, these are a physical realisation of quantum bits
+ based upon what are known as superconducting interference devices (SQUIDs), and attempt to find properties of the wavefunction of the molecule
+ (in this case molecular Hydrogen).
 
@@
 One of the reasons that developing new approaches to tackling electronic structure calculations is of importance is that they are extremely
-computationally expensive.
-Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems in nature by using quantum systems.
-A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum
+computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems in
+nature by using quantum systems. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum
  hardware and software that will allow for efficient quantum simulations of chemical systems. A problem of tantamount importance in quantum chemistry

### 2019-06-21 article.tex
quote abolfazl in non-tech background

@@
 nature by using quantum systems. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum
- hardware and software that will allow for efficient quantum simulations of chemical systems. A problem of tantamount importance in quantum chemistry
+ hardware and software that will allow for efficient quantum simulations of chemical systems. Dr Abolfazl Bayat of the Controlled
+ Quantum Dynamics research group at UCL states that "noise-resilient quantum computers would have transformative effects in many fields, but especially
+  in quantum chemistry where efficient quantum simulations would represent a significant leap forward for the field". A problem of tantamount importance in quantum chemistry
  is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy eigenvalues define a great deal of properties of

### 2019-06-21 article.tex
miki U quote

@@
 \section{Conclusion and outlook}
+
 As this is the first scalable simulation of molecular energies on any type of quantum hardware it represents an important step in the history of
@@
  where classical techniques fail in solving traditionally intractable problems.
+
+ Mikolaj Uryszek, a researcher in the Strongly Correlated Electron Systems group at UCL, commented that "variational techniques in quantum chemistry
+ are becoming increasingly prevalent as a useful benchmarking tool for Noisy Intermediate-Scale Quantum devices, and this paper by O’Malley et al.
+ represents one of the most accurate quantum chemistry simulations to date, and is a certainly a promising validation of the development of
+ superconducting qubits for scalable quantum hardware".
 

### 2019-06-21 article.tex
update quote and conclusion

--- 2019-06-21 article.tex
@@
 
+ Mikolaj Uryszek, a researcher in the Strongly Correlated Electron Systems group at UCL, commented that "variational techniques in quantum chemistry
+ are becoming increasingly prevalent as a useful benchmarking tool these early stage Quantum devices, and this paper by O’Malley et al.
+ represents one of the most accurate quantum chemistry simulations using quantum hardware to date, and is a certainly a promising validation of the
+  development of superconducting qubits for scalable quantum hardware".
+
 Late last year the US passed the new National Quantum Initiative Act pledging around \textdollar1.2 billion in funding for quantum information science
@@
  the importance of this work in quantum chemistry simulations cannot be overstated. As aside from the much touted almost pop-science status of
- quantum encryption, the myriad opportunities afforded by more efficient scalable quantum chemistry simulations looms large in garnering serious
- investor interest. The ability to run quantum simulations of the behaviour of molecules and materials is hoped offer new avenues for increasing
- our understanding of chemistry and enable the development of new medicines and materials in silico.
+ quantum encryption and communication, the myriad opportunities afforded by more efficient and scalable quantum chemistry simulations looms large
+ in garnering serious investor interest. The ability to run quantum simulations of the behaviour of molecules and materials is hoped offer new
+ avenues for increasing our understanding of chemistry and enable the development of new medicines and materials in silico.
 

### 2019-06-21 article.tex
dan browne quotes

@@
  Although a quantum simulation such as the VQE is almost foolproof it may still not be adequate to calculate exact numerical solutions that are
-characteristic of various types of molecules and their interactions. Quantum computing shows promise to eliminate such errors whilst using a
-larger number of qubits. However, these factors work against each other. If such a machine can be built, there would be more states and thus
-information to manipulate whilst withstanding error. This could revolutionise applications such as pharmaceuticals where cures and treatments
- for complex or incurable diseases such as Cancer, Prion disease and so forth could be engineered. If (or when should I say) this is possible,
-  we would have a machine taking on the roles of a chemist, problem solver and designer simultaneously and combined into one entity!
+ characteristic of various types of molecules and their interactions. It’s hard to calculate energies to make such landscapes - Professor of Physics
+ Dan Browne at University College London proposed that although VQE has a much simpler quantum circuit it still uses a classical search as part of
+ the process to find these molecular energies. “VQE will only work If you have prior knowledge - this helps to refine the search. In the search, you
+ need to look in the right place.” He also commented “one could try combining both methods to make a better algorithm”. Could combining PEA and VQE
+ conjure up a huge amount of benefits so much that it reduces flaws such as noise and error intolerance?
+
+ Quantum computing shows promise to eliminate such errors whilst using a larger number of qubits. However, these factors work against each other.
+ If such a machine can be built, there would be more states and thus information to manipulate whilst withstanding error. This could revolutionise
+ applications such as pharmaceuticals where cures and treatments for complex or incurable diseases such as Cancer, Prion disease and so forth could
+ be engineered. If (or when should I say) this is possible,  we would have a machine taking on the roles of a chemist, problem solver and designer
+  simultaneously and combined into one entity!
 
@@
  Mikolaj Uryszek, a researcher in the Strongly Correlated Electron Systems group at UCL, commented that "variational techniques in quantum chemistry
- are becoming increasingly prevalent as a useful benchmarking tool these early stage Quantum devices, and this paper by O’Malley et al.
+ are becoming increasingly prevalent as a useful benchmarking tool to compare these early stage Quantum devices, and this paper by O’Malley et al.
  represents one of the most accurate quantum chemistry simulations using quantum hardware to date, and is a certainly a promising validation of the
@@
  quantum encryption and communication, the myriad opportunities afforded by more efficient and scalable quantum chemistry simulations looms large
- in garnering serious investor interest. The ability to run quantum simulations of the behaviour of molecules and materials is hoped offer new
+ in garnering serious investor interest. The ability to run quantum simulations of the behaviour of atoms and molecules is hoped offer new
  avenues for increasing our understanding of chemistry and enable the development of new medicines and materials in silico.

### 2019-06-21 article.tex
update non-tech section

@@
 \section{Introduction}
-“Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical, and by golly it's a wonderful
+``Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical, and by golly it's a wonderful
  problem, because it doesn't look so easy.” Richard Feynman’s words are as true today as when he spoke them almost forty years ago.
+ And it is this opinion of Feynman among others which prompted the enormous effort that has been expended on the development of quantum computing
+ since then. The paper `Scalable Quantum Simulation of Molecular Energies' by O’Malley et al. is evidence of just how far the technology
+  has come in this time, and indicates what we might expect from superconducting quantum computing technologies in the future.
 
@@
 The building blocks of any quantum computing process may be considered to be qubits. A qubit, or quantum bit, is the quantum analogue of the
-classical bit in which classical information is encoded in 0s and 1s. So the qubit represents a quantum superposition or simultaneous combination of
-both a predetermined ‘0’ and a ‘1’ state. The quantum algorithms were run on superconducting qubits, these are a physical realisation of quantum bits
- based upon what are known as superconducting interference devices (SQUIDs), and attempt to find properties of the wavefunction of the molecule
- (in this case molecular Hydrogen).
+classical bit in which classical information is encoded in 0s and 1s. So the qubit represents a quantum superposition, or simultaneous combination, of
+both a predetermined `0’ and a `1’ state. In paper by O’Malley et al., the quantum algorithms were run on superconducting qubits. These are a
+physical realisation of quantum bits based upon what are known as superconducting quantum interference devices (SQUIDs), and they are used here
+to find properties of the wavefunction of molecular Hydrogen.
 
@@
 One of the reasons that developing new approaches to tackling electronic structure calculations is of importance is that they are extremely
-computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems in
-nature by using quantum systems. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum
- hardware and software that will allow for efficient quantum simulations of chemical systems. Dr Abolfazl Bayat of the Controlled
- Quantum Dynamics research group at UCL states that "noise-resilient quantum computers would have transformative effects in many fields, but especially
-  in quantum chemistry where efficient quantum simulations would represent a significant leap forward for the field". A problem of tantamount importance in quantum chemistry
- is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy eigenvalues define a great deal of properties of
- interest in the molecule. This is of great importance in for example the development of pharmaceuticals where companies have an extremely laborious
- testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings
- and would better ensure that the pharmaceutical under development behaved as required prior to starting trials.
+computationally expensive. Indeed one of the original motivations for advancing the field of quantum computing was the desire to simulate quantum
+ systems in nature through the use of quantum systems, and by so doing to circumvent the exponential computing power needed to do these simulations
+ on classical hardware. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum hardware
+ and software that will allow for efficient quantum simulations of quantum chemical systems. Dr Abolfazl Bayat, a researcher at the Controlled
+ Quantum Dynamics research group at UCL, states that "noise-resilient quantum computers would have transformative effects upon many fields,
+ but especially in quantum chemistry where efficient quantum simulations would represent a significant leap forward for the field". A problem of
+ tantamount importance in quantum chemistry is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy
+ eigenvalues define a great deal of properties of interest in the molecule. This is of great importance in for example the development of
+ pharmaceuticals where companies have an extremely laborious testing and trials process, if a significant part of the initial testing process
+ could be done in silico - this would represent significant savings and would better ensure that the pharmaceutical under development behaved as
+ required prior to starting trials.
 

### 2019-06-21 article.tex
general updates

@@
 
-Now there are a number of different approaches to building physical quantum computing hardware being pursued by various research groups
-and companies, each with their own pros and cons. Some of the types of implemented qubits include trapped ions, nitrogen-vacancy centres,
- quantum silicon photonics and superconducting, to name but a few. The type used here is the Xmon transmon qubit, a superconducting qubit
-  built around a superconducting quantum interference device, or SQUID. Variations of the superconducting qubit are being developed by
-  companies such as D-wave, IBM and Rigetti in the current race for quantum supremacy.
+There are a number of different approaches to building physical quantum computing hardware being pursued by various research groups and companies,
+each with their own advantages and disadvantages. Some of the types of experimentally implemented qubits include trapped ions, nitrogen-vacancy centres,
+ quantum silicon photonics and superconducting, to name but a few. The qubits used to implement the both phase estimation algorithm and the variational
+  quantum eigensolver were Xmon transmon qubits, a superconducting qubit built around a superconducting quantum interference device, or SQUID.
+  A SQUID is made of a superconducting loops and Josephson junctions. The state of a qubit is determined by how many pairs of electrons tunnel
+  across the Josephson junctions. Variations of the superconducting qubit are being developed by companies such as D-wave, IBM and Rigetti in the
+  current race for quantum supremacy.
 
@@
 \fbox{\begin{minipage}[c]{31em}%
-\centerline{\textbf{Experimental realisation (SQUID)}}
-The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of
-superconducting interference device or SQUID. It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are
-charge states, and the superposition of these charge states is tuned using microwave resonators. The Xmon qubit has a number of favourable features,
- which include easy fabrication, fast qubit control and long qubit coherence times.
+\centerline{\textbf{Experimental Implementation of Quantum Hardware}}
+
+The physical quantum hardware used to implement the VQE and PEA algorithms are Xmon qubits. The Xmon qubit is a variation of the transmon qubit,
+a class superconducting qubit which uses superconducting quantum interference devices, also known as SQUIDs. It is a type of charge qubit, which is
+to say it is a qubit where it’s `0’ and `1’ basis states are charge states, and the superposition of these charge states is tuned using microwave
+resonators. The Xmon qubit has a number of favourable features, which include easy fabrication, fast qubit control and long qubit coherence times.
 
@@
 quantum computing applications. The results indicate that for near-term quantum devices without effective error correction the adaptive approach
-represented by the Variational Quantum Eigensolver may have better error resilience than that of standard gate model approach represented by the
-Phase Estimation Algorithm. The expectation is that this work will pave the way for the development of further techniques for intractable calculations
+represented by the variational quantum eigensolver may have better error resilience than that of standard gate model approach represented by the
+phase estimation algorithm. The expectation is that this work will pave the way for the development of further quantum techniques for calculations
  in quantum chemistry. And the final aim is that eventually these variational quantum chemistry techniques will allow for numerically exact simulations
-  of chemical reaction rates, which are of great industrial commercial value. In particular, the efficiency - requiring only short state preparation
- and measurement procedures, and so it is without the normal substantial overhead required for quantum error correction - and robustness to
- error displayed by the experimental implementation of the variational quantum eigensolver technique indicates that this technique might succeed
- where classical techniques fail in solving traditionally intractable problems.
+  of chemical reaction rates, which are of great industrial commercial value. The VQE requires only short state preparation
+ and measurement procedures, and so it is without the normal substantial overhead required for quantum error correction. This improves the efficiency
+ and robustness to error displayed by the experimental implementation of the variational quantum eigensolver technique indicates that this technique
+  might succeed where classical techniques fail in solving traditionally intractable problems.
 
  Mikolaj Uryszek, a researcher in the Strongly Correlated Electron Systems group at UCL, commented that "variational techniques in quantum chemistry
- are becoming increasingly prevalent as a useful benchmarking tool to compare these early stage Quantum devices, and this paper by O’Malley et al.
- represents one of the most accurate quantum chemistry simulations using quantum hardware to date, and is a certainly a promising validation of the
-  development of superconducting qubits for scalable quantum hardware".
+ are becoming increasingly prevalent as a useful benchmarking tool to compare these early stage quantum devices, and this paper by O’Malley et al.
+ represents one of the most accurate quantum chemistry simulations using quantum hardware to date, and is a promising validation of the
+  development of superconducting qubits for scalable quantum hardware". And it certainly heralds an interesting future for the use both of
+  superconducting qubits and variational quantum algorithms for tackling classically intractable problems in quantum chemistry and beyond.
 
@@
  Europe and also in the US and China, aiming to fast-track quantum technologies out of university research groups and into industrial applications,
- the importance of this work in quantum chemistry simulations cannot be overstated. As aside from the much touted almost pop-science status of
+ the importance of this work in quantum chemistry cannot be overstated. As aside from the much touted almost pop-science status of
  quantum encryption and communication, the myriad opportunities afforded by more efficient and scalable quantum chemistry simulations looms large
- in garnering serious investor interest. The ability to run quantum simulations of the behaviour of atoms and molecules is hoped offer new
- avenues for increasing our understanding of chemistry and enable the development of new medicines and materials in silico.
+ in garnering serious investor interest. The ability to run quantum simulations of the behaviour of atoms and molecules is hoped to offer new
+ avenues for increasing our understanding of chemistry and enable the development of new medicines and materials in silico, thereby reducing
+ the need for expensive trial-and-error approaches to research and development.
 

### 2019-06-21 article.tex
general updates1

@@
 each with their own advantages and disadvantages. Some of the types of experimentally implemented qubits include trapped ions, nitrogen-vacancy centres,
- quantum silicon photonics and superconducting, to name but a few. The qubits used to implement the both phase estimation algorithm and the variational
+ quantum silicon photonics and superconducting, to name but a few. The qubits used to implement both the phase estimation algorithm and the variational
   quantum eigensolver were Xmon transmon qubits, a superconducting qubit built around a superconducting quantum interference device, or SQUID.

### 2019-06-21 article.tex
box par fix.

--- 2019-06-21 article.tex
@@
 $\frac{\ket{0} + \ket{1}}{\sqrt 2}$, second, our initial state. Since we can evolve states by unity operator. By inputting both parts of qubits
-onto a multiple controlled-U gate, the eigenvalue of each unitary $\hat{U}$ will transform to each one of qubits in first part.
+onto a multiple controlled-U gate, the eigenvalue of each unitary $\hat{U}$ will transform to each one of qubits in first part.\bigskip
 
@@
 \]
-\end{footnotesize}
+\end{footnotesize}%
 As we can see, the result of QFT is just the first part of qubits we prepared.

### 2019-06-21 article.tex
general updates2

--- 2019-06-21 article.tex
@@
  Dan Browne at University College London proposed that although VQE has a much simpler quantum circuit it still uses a classical search as part of
- the process to find these molecular energies. “VQE will only work If you have prior knowledge - this helps to refine the search. In the search, you
+ the process to find these molecular energies. ``VQE will only work If you have prior knowledge - this helps to refine the search. In the search, you
  need to look in the right place.” He also commented “one could try combining both methods to make a better algorithm”. Could combining PEA and VQE
@@
 
- Mikolaj Uryszek, a researcher in the Strongly Correlated Electron Systems group at UCL, commented that "variational techniques in quantum chemistry
+ Mikolaj Uryszek, a researcher in the Strongly Correlated Electron Systems group at UCL, commented that ``variational techniques in quantum chemistry
  are becoming increasingly prevalent as a useful benchmarking tool to compare these early stage quantum devices, and this paper by O’Malley et al.

### 2019-06-21 article.tex
general updates3

@@
  and software that will allow for efficient quantum simulations of quantum chemical systems. Dr Abolfazl Bayat, a researcher at the Controlled
- Quantum Dynamics research group at UCL, states that "noise-resilient quantum computers would have transformative effects upon many fields,
+ Quantum Dynamics research group at UCL, states that ``noise-resilient quantum computers would have transformative effects upon many fields,
  but especially in quantum chemistry where efficient quantum simulations would represent a significant leap forward for the field". A problem of

### 2019-06-21 article.tex
general updates4

@@
  quantum silicon photonics and superconducting, to name but a few. The qubits used to implement both the phase estimation algorithm and the variational
-  quantum eigensolver were Xmon transmon qubits, a superconducting qubit built around a superconducting quantum interference device, or SQUID.
-  A SQUID is made of a superconducting loops and Josephson junctions. The state of a qubit is determined by how many pairs of electrons tunnel
-  across the Josephson junctions. Variations of the superconducting qubit are being developed by companies such as D-wave, IBM and Rigetti in the
+  quantum eigensolver were Xmon transmon qubits, a type of superconducting charge qubit built around a superconducting quantum interference device, or SQUID.
+  Variations of the superconducting qubit are being developed by companies such as D-wave, IBM and Rigetti in the
   current race for quantum supremacy.

### 2019-06-21 article.tex
general updates5

@@
 
-\section{Non-technical background}
+\section{Scientific Background}
 
@@
 
-\section{Techniques in paper}
+\section{Techniques in Paper}
 If I asked you how to make a cup of coffee, your response would go a little something like this; prepare a cup (clean of course), put a number of
@@
 
-\subsection{The Experimental Implementation}
+\subsection{Experimental Implementation}
 
@@
 
-\section{Conclusion and outlook}
+\section{Conclusion and Outlook}
 
@@
 
+\section{Afterword}
+
+Shuhao Yang wrote the Introduction and History sections and the PEA section and box. James Mills wrote the Scientific Background and Conclusion
+and Outlook sections and the Experimental Implementation section and box. Shanice St John wrote the Techniques in Paper section introduction and
+the Main Achievement of Paper section, and the VQE section and box. However we all edited and redrafted together and interviewed the academics
+whose opinions we quoted in the article. We would like to thank Dr Abolfazl Bayat, Prof. Dan Browne and Mikolaj Uryszek for kindly talking to
+us and allowing us to quote them here.
+
 \bibliography{ref}

### 2019-06-21 article.tex
change on final section and diagram position.

@@
  has been decided that either a new blend of coffee is necessary as the current coffee might be perhaps too strong!
-
-This process is repeated a number of times until the estimate energy approaches a specific value.
-The final result is an approximation of the smallest eigenenergy.
-Figure \ref{VQE} illustrates the key outline of the VQE algorithm.
 \begin{figure}[H]
@@
 \end{figure}
+This process is repeated a number of times until the estimate energy approaches a specific value.
+The final result is an approximation of the smallest eigenenergy.
+Figure \ref{VQE} illustrates the key outline of the VQE algorithm.
 
@@
 
-Shuhao Yang wrote the Introduction and History sections and the PEA section and box. James Mills wrote the Scientific Background and Conclusion
+This article is inspired by Scalable quantum simulation of molecular energies \cite{o2016scalable}.
+Shuhao Yang wrote the Introduction and History sections and the PEA section and box.
+James Mills wrote the Scientific Background and Conclusion
 and Outlook sections and the Experimental Implementation section and box. Shanice St John wrote the Techniques in Paper section introduction and

### 2019-06-21 article.tex
add few ref.

@@
  And it is this opinion of Feynman among others which prompted the enormous effort that has been expended on the development of quantum computing
- since then. The paper `Scalable Quantum Simulation of Molecular Energies' by O’Malley et al. is evidence of just how far the technology
+ since then. The paper `Scalable Quantum Simulation of Molecular Energies' \cite{o2016scalable} by O’Malley et al. is evidence of just how far the technology
   has come in this time, and indicates what we might expect from superconducting quantum computing technologies in the future.
@@
 classical bit in which classical information is encoded in 0s and 1s. So the qubit represents a quantum superposition, or simultaneous combination, of
-both a predetermined `0’ and a `1’ state. In paper by O’Malley et al., the quantum algorithms were run on superconducting qubits. These are a
+both a predetermined `0’ and a `1’ state. In paper \cite{o2016scalable} by O’Malley et al., the quantum algorithms were run on superconducting qubits. These are a
 physical realisation of quantum bits based upon what are known as superconducting quantum interference devices (SQUIDs), and they are used here

### 2019-06-21 article.tex
changes
minors change in final section.
add more quotes.

@@
 \section{Main Achievement of paper}
-As it is known, building a quantum computer comes with many challenges, one being the aspect of scalability. One of the advantages of using PEA to
+As it is known, building a quantum computer comes with many challenges, one being the aspect of scalability.
+As the number of qubits increases, it becomes increasingly difficult to solve chemical rates.
+Senior research fellow Dr Lluis Masanes at University College London commented “Many quantum simulators such as the ion trap give good results but they are not scalable”.
+Adding more degrees of freedom, becomes computationally challenging and thus impossible to solve classically.
+
+One of the advantages of using PEA to
 compute electronic structures of a molecule is better asymptotic scaling which would prove useful for larger molecules than Hydrogen. However, this
@@
 James Mills wrote the Scientific Background and Conclusion
-and Outlook sections and the Experimental Implementation section and box. Shanice St John wrote the Techniques in Paper section introduction and
-the Main Achievement of Paper section, and the VQE section and box. However we all edited and redrafted together and interviewed the academics
-whose opinions we quoted in the article. We would like to thank Dr Abolfazl Bayat, Prof. Dan Browne and Mikolaj Uryszek for kindly talking to
+and Outlook sections and the Experimental Implementation section and box.
+Shanice St John wrote the Techniques in Paper section introduction and the Main Achievement of Paper section, and the VQE section and box.
+However we all edited and redrafted together and interviewed the academics
+whose opinions we quoted in the article. We would like to thank Dr Abolfazl Bayat, Prof. Dan Browne, Mikolaj Uryszek and Dr Lluis Masanes for kindly talking to
 us and allowing us to quote them here.
